---
title: "FV analyses"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.path = "figs/", dpi = 300, colormodel = "cmyk")
options(scipen = 999)
```

# load packages
```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(knitr)
library(MuMIn)
library(cowplot)
library(broom)
library(tidystringdist)
```

# define color palettes
```{r}
algorithm = c("#006989", "#FEC601", "#F43C13", "#00A5CF", "#00A878")
food = c("#A4C960", "#2A5C8C")
liking = c("#FF0000", "#F2AD00")
bid = c("#00A08A", "#F2AD00", "#F98400", "#FF0000", "#A80000")
dc_bw = readRDS("~/dc_bw.Rds") +
    theme(text = element_text(size = 13, family = "Futura Medium"))
```

# load and tidy data
```{r}
partial = readRDS("FV_partial_validation.RDS") %>%
  mutate(sample = "partial validation",
         run = "run1") %>%
  select(sample, subjectID, run, trial, health, bid, rt, algorithm, dotProduct, dotSTD)

complete = readRDS("FV_complete_validation.RDS") %>%
  mutate(sample = "complete validation") %>%
  filter(!liking_rating < 1) %>%
  select(sample, subjectID, run, trial, health, liking, bid, rt, algorithm, dotProduct, dotSTD)

data = bind_rows(partial, complete) %>%
  arrange(subjectID, trial) %>%
  filter(!is.na(bid)) %>%
  mutate(sample = factor(sample, levels = c("partial validation", "complete validation")),
         type = ifelse(grepl("logistic", algorithm), "multivariate", "univariate"),
         algorithm = gsub("rest", "baseline", algorithm),
         algorithm = factor(algorithm, levels = c("logistic classifier", "regulate > look", "regulate > baseline")))
```

# descriptives
## number of participants
```{r}
data %>%
  filter(algorithm == "logistic classifier") %>%
  select(sample, subjectID) %>%
  unique() %>%
  group_by(sample) %>%
  summarize(n = n())
```

## pattern expression values
```{r, fig.width=7, fig.height=8}
data %>%
  group_by(sample, algorithm, health) %>%
  summarize(n = n(),
            mean = round(mean(dotSTD, na.rm = TRUE), 2),
            sd = round(sd(dotSTD, na.rm = TRUE), 2),
            min = min(dotSTD, na.rm = TRUE),
            max = max(dotSTD, na.rm = TRUE))

data %>%
  group_by(sample, algorithm, health) %>%
  summarize(n = n(),
            mean = round(mean(dotSTD, na.rm = TRUE), 2),
            sd = round(sd(dotSTD, na.rm = TRUE), 2)) %>%
  gather(variable, value, mean, sd) %>%
  unite(algorithm, c(algorithm, variable), sep = " ") %>%
  spread(algorithm, value) %>%
  group_by(sample, health) %>%
  fill(everything(), .direction = "up") %>%
  fill(everything(), .direction = "down") %>%
  unique() %>%
  kable(format = "pandoc")

a = data %>%
  group_by(health, sample, algorithm) %>%
  mutate(mean = mean(dotSTD, na.rm = TRUE)) %>%
  ggplot(aes(dotSTD, fill = health)) +
    geom_density(color = NA, alpha = .7) +
    geom_vline(aes(xintercept = mean, color = health), alpha = .7) +
    facet_grid(sample~type + algorithm, scales = "free_x") +
    scale_fill_manual(name = "", values = food) + 
    scale_color_manual(name = "", values = food) + 
    scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks(3)) +
    scale_x_continuous(breaks = scales::pretty_breaks(3)) +
    labs(x = "\nstandardized regulation PEV", y = "density\n") + 
    dc_bw +
    theme(legend.position = "top")

b = data %>%
  group_by(algorithm, subjectID, health) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE)) %>%
  group_by(health, sample, algorithm) %>%
  mutate(mean = mean(meanPEV, na.rm = TRUE)) %>%
  ggplot(aes(meanPEV, fill = health)) +
    geom_density(color = NA, alpha = .7) +
    geom_vline(aes(xintercept = mean, color = health), alpha = .7) +
    facet_grid(sample~type + algorithm, scales = "free_x") +
    scale_fill_manual(name = "", values = food) + 
    scale_color_manual(name = "", values = food) + 
    scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks(3)) +
    scale_x_continuous(breaks = scales::pretty_breaks(3)) +
    labs(x = "\nparticipant mean standardized regulation PEV", y = "density\n") + 
    dc_bw +
    theme(legend.position = "none")

plot_grid(a, b, ncol = 1, align = "v", labels = c('A', 'B'))
```

* `rmcorr` messes with the `lmer` models, so it is commented out here to avoid that issue
```{r}
# data %>%
#   select(sample, subjectID, trial, algorithm, dotSTD) %>%
#   spread(algorithm, dotSTD) %>%
#   mutate(subjectID = as.factor(subjectID)) %>%
#   unique() %>%
#   ungroup() %>%
#   nest(-c(sample)) %>% 
#   mutate(`logistic classifier_regulate > look` = map(data, ~ rmcorr::rmcorr(subjectID, `logistic classifier`, `regulate > look`, .)),
#          `regulate > baseline_logistic classifier` = map(data, ~ rmcorr::rmcorr(subjectID, `logistic classifier`, `regulate > baseline`, .)),
#          `regulate > look_regulate > baseline` = map(data, ~ rmcorr::rmcorr(subjectID, `regulate > baseline`, `regulate > look`, .))) %>%
#   gather(test, model, contains("reg")) %>%
#   group_by(sample, test) %>%
#   mutate(r = sprintf("%s [%s, %s]", round(model[[1]][[1]], 2), round(model[[1]][[4]][1], 2), round(model[[1]][[4]][2], 2)),
#          df = model[[1]][[2]],
#          p = round(model[[1]][[3]], 3),
#          p = ifelse(p == 0, "< .001", as.character(p))) %>%
#   ungroup() %>%
#   select(sample, test, r, df) %>%
#   extract(test, c("var1", "var2"), "(.*)_(.*)") %>%
#   spread(var1, r) %>%
#   select(sample, var2, df, `regulate > baseline`, everything()) %>%
#   kable(format = 'pandoc')
```

# visualize
## health
```{r, fig.width=10, fig.height=8.5}
a = data %>%
  ggplot(aes(health, dotSTD, fill = health, alpha = sample)) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    facet_grid(~type + algorithm) +
    scale_fill_manual(name = "", values = food) + 
    scale_alpha_discrete(name = "", range = c(.6, 1)) +
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = c(.355 , .925),
          legend.box = "horizontal",
          text = element_text(size = 12),
          legend.spacing.x = unit(0.1, 'cm'))
  
b = data %>%
  filter(!is.na(bid)) %>%
  ggplot(aes(health, dotSTD)) +
    stat_summary(aes(group = subjectID), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = 1), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = health), fun.data = mean_cl_boot,  geom = "pointrange", width = 0) + 
    facet_grid(sample~type + algorithm) +
    scale_color_manual(name = "", values = food) +
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    coord_cartesian(ylim = c(-1.1, 1)) +
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none",
          text = element_text(size = 12))

c = data %>%
  filter(sample == "complete validation") %>%
  ggplot(aes(liking, dotSTD, fill = health)) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    facet_grid(~type + algorithm) +
    scale_fill_manual(name = "", values = food) + 
    scale_alpha_discrete(name = "", range = c(.6, 1)) +
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none", #legend.position = c(.15, .925),
          legend.box = "horizontal",
          text = element_text(size = 12))

d = data %>%
  filter(sample == "complete validation") %>%
  ggplot(aes(liking, dotSTD)) +
    stat_summary(aes(group = interaction(subjectID, health), color = health), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = health, color = health), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = health), fun.data = mean_cl_boot, geom = "pointrange", width = 0) + 
    facet_grid(~type + algorithm) +
    scale_color_manual(name = "", values = food) + 
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    coord_cartesian(ylim = c(-1.1, 1)) + 
    labs(y = "standarized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none",
          text = element_text(size = 12))

plot_grid(a, b, c, d, ncol = 2, align = "v", labels = c('A', 'B', 'C', 'D'))
```

## bid value
```{r, fig.width=15.5, fig.height=9}
a = data %>%
  group_by(sample, bid, algorithm) %>%
  mutate(n.obs = n()) %>%
  ggplot(aes(as.factor(bid), dotSTD, color = algorithm)) +
    stat_summary(aes(group = algorithm), fun.y = mean, geom = "line") +
    stat_summary(fun.data = mean_cl_boot, geom = "linerange") +
    stat_summary(aes(size = n.obs), fun.y = mean, geom = "point") +
    scale_color_manual(name = "", values = algorithm) + 
    scale_size(name = "", range = c(.5,3), breaks = c(600, 900, 1200)) + 
    facet_grid(sample~., scales = "free_x") + 
    labs(x = "\nbid value", y = "standardized regulation PEV\n") + 
    dc_bw +
    theme(legend.position = "top",
          legend.box = "vertical")

b = data %>%
  mutate(bid.bin = ifelse(sample == "partial validation" & bid > 1, "high", 
                   ifelse(sample == "partial validation" & bid < 1, "low",
                   ifelse(sample == "complete validation" & bid >= 1, "high",
                   ifelse(sample == "complete validation" & bid < 1, "low", NA)))),
         bid.bin = factor(bid.bin, levels = c("low", "high"))) %>%
  filter(!is.na(bid.bin)) %>%
  ggplot(aes(bid.bin, dotSTD)) +
    stat_summary(aes(group = subjectID), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = 1), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = bid.bin), fun.data = mean_cl_boot, geom = "pointrange", width = 0) + 
    facet_grid(sample~type + algorithm) +
    scale_color_manual(name = "", values = liking) + 
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    coord_cartesian(ylim = c(-1.2, 1.2)) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none")

c = data %>%
  mutate(bid.bin = ifelse(sample == "partial validation" & bid > 1, "high", 
                   ifelse(sample == "partial validation" & bid < 1, "low",
                   ifelse(sample == "complete validation" & bid >= 1, "high",
                   ifelse(sample == "complete validation" & bid < 1, "low", NA)))),
         bid.bin = factor(bid.bin, levels = c("low", "high"))) %>%
  filter(!is.na(bid.bin)) %>%
  ggplot(aes(bid.bin, dotSTD)) +
    stat_summary(aes(group = interaction(subjectID, health), color = health), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = health, color = health), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = health), fun.data = mean_cl_boot, geom = "pointrange", width = 0) + 
    facet_grid(sample~type + algorithm) +
    scale_color_manual(name = "", values = food) + 
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    coord_cartesian(ylim = c(-1.2, 1.2)) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none")

d = data %>%
  filter(sample == "complete validation") %>%
  filter(liking == "liked") %>%
  mutate(bid.bin = ifelse(bid >= 1, "high", "low"),
         bid.bin = factor(bid.bin, levels = c("low", "high")),
         sample = "complete validation liked only") %>%
  ggplot(aes(bid.bin, dotSTD)) +
    stat_summary(aes(group = subjectID), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = 1), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = bid.bin), fun.data = mean_cl_boot, geom = "pointrange", width = 0) + 
    facet_grid(sample~type + algorithm) +
    scale_color_manual(name = "", values = liking) + 
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    coord_cartesian(ylim = c(-1.2, 1.2)) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none")

e = data %>%
  filter(sample == "complete validation") %>%
  filter(liking == "liked") %>%
  mutate(bid.bin = ifelse(bid >= 1, "high", "low"),
         bid.bin = factor(bid.bin, levels = c("low", "high")),
         sample = "complete validation liked only") %>%
  ggplot(aes(bid.bin, dotSTD)) +
    stat_summary(aes(group = interaction(subjectID, health), color = health), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = health, color = health), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = health), fun.data = mean_cl_boot, geom = "pointrange", width = 0) + 
    facet_grid(sample~type + algorithm) +
    scale_color_manual(name = "", values = food) + 
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    coord_cartesian(ylim = c(-1.2, 1.2)) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = c(.88, .15))

middle_row = plot_grid(b, d, labels = c('B', 'D'), ncol = 1, rel_widths = c(1, 1))
bottom_row = plot_grid(c, e, labels = c('C', 'E'), ncol = 1, rel_widths = c(1, 1))
plot_grid(a, middle_row, bottom_row, labels = c('A', '', ''), ncol = 3, rel_widths = c(1, 1, 1))
```

# health, palatability, and bid effects
```{r}
fit_mod = function(data){
    mod = lmer(dotSTD ~ health + (1 | subjectID), data = data)
    return(mod)
}

data %>%
  filter(algorithm == "regulate > baseline") %>%
  nest(-c(sample, type)) %>%
  mutate(
    test = map(data, fit_mod),
    tidied = map(test, broom.mixed::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE) %>%
  filter(effect == "fixed")  %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, estimate - (1.96 * std.error), estimate + (1.96 * std.error)),
         term = gsub("\\(Intercept\\)", "intercept", term),
         term = gsub("healthunhealthy", "food type", term)) %>%
  select(sample, type, term, df, `b [95% CI]`) %>%
  rename("Sample" = sample,
         "Signature Type" = type) %>%
  kable(format = "pandoc", digits = 2)
```

```{r}
fit_mod = function(data){
    mod = lmer(dotSTD ~ liking + (1 | subjectID), data = data)
    return(mod)
}

data %>%
  filter(algorithm == "regulate > baseline") %>%
  filter(sample == "complete validation") %>%
  nest(-c(sample, type)) %>%
  mutate(
    test = map(data, fit_mod),
    tidied = map(test, broom.mixed::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE) %>%
  filter(effect == "fixed")  %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, estimate - (1.96 * std.error), estimate + (1.96 * std.error)),
         term = gsub("\\(Intercept\\)", "intercept", term),
         term = gsub("likingliked", "liking", term)) %>%
  select(sample, type, term, df, `b [95% CI]`) %>%
  rename("Sample" = sample,
         "Signature Type" = type) %>%
  kable(format = "pandoc", digits = 2)
```

```{r}
fit_mod = function(data){
    mod = lmer(dotSTD ~ health*liking + (1 | subjectID), data = data)
    return(mod)
}

data %>%
  filter(algorithm == "regulate > baseline") %>%
  filter(sample == "complete validation") %>%
  nest(-c(sample, type)) %>%
  mutate(
    test = map(data, fit_mod),
    tidied = map(test, broom.mixed::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE) %>%
  filter(effect == "fixed")  %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, estimate - (1.96 * std.error), estimate + (1.96 * std.error)),
         term = gsub("\\(Intercept\\)", "intercept", term),
         term = gsub("healthunhealthy", "food type", term),
         term = gsub("likingliked", "liking", term),
         term = gsub(":liking", " x liking", term)) %>%
  select(sample, type, term, df, `b [95% CI]`) %>%
  rename("Sample" = sample,
         "Signature Type" = type) %>%
  kable(format = "pandoc", digits = 2)
```

```{r}
fit_mod = function(data){
    mod = lmer(dotSTD ~ bid_c + (1 | subjectID), data = data)
    return(mod)
}

# complete and partial validation
data %>%
  filter(algorithm == "regulate > baseline") %>%
  group_by(subjectID, type) %>%
  mutate(bid_c = bid - mean(bid, na.rm = TRUE)) %>%
  ungroup() %>%
  nest(-c(sample, type)) %>%
  mutate(
    test = map(data, fit_mod),
    tidied = map(test, broom.mixed::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE) %>%
  filter(effect == "fixed")  %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, estimate - (1.96 * std.error), estimate + (1.96 * std.error)),
         term = gsub("\\(Intercept\\)", "intercept", term),
         term = gsub("bid_c", "bid", term)) %>%
  select(sample, type, term, df, `b [95% CI]`) %>%
  rename("Sample" = sample,
         "Signature Type" = type) %>%
  kable(format = "pandoc", digits = 2)

# complete validation, liked only
data %>%
  filter(algorithm == "regulate > baseline") %>%
  filter(sample == "complete validation") %>%
  filter(liking == "liked") %>%
  group_by(subjectID, type) %>%
  mutate(bid_c = bid - mean(bid, na.rm = TRUE)) %>%
  ungroup() %>%
  nest(-c(sample, type)) %>%
  mutate(
    test = map(data, fit_mod),
    tidied = map(test, broom.mixed::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE) %>%
  filter(effect == "fixed")  %>%
  mutate(`b [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, estimate - (1.96 * std.error), estimate + (1.96 * std.error)),
         term = gsub("\\(Intercept\\)", "intercept", term),
         term = gsub("bid_c", "bid", term)) %>%
  select(sample, type, term, df, `b [95% CI]`) %>%
  rename("Sample" = sample,
         "Signature Type" = type) %>%
  kable(format = "pandoc", digits = 2)
```

```{r}
fit_mod = function(data){
    mod = lmer(dotSTD ~ health*bid_c + (1 | subjectID), data = data)
    return(mod)
}

# complete and partial validation
data %>%
  filter(algorithm == "regulate > baseline") %>%
  group_by(subjectID, type) %>%
  mutate(bid_c = bid - mean(bid, na.rm = TRUE)) %>%
  ungroup() %>%
  nest(-c(sample, type)) %>%
  mutate(
    test = map(data, fit_mod),
    tidied = map(test, broom.mixed::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE) %>%
  filter(effect == "fixed")  %>%
  mutate(`Mdiff [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, estimate - (1.96 * std.error), estimate + (1.96 * std.error)),
         term = gsub("\\(Intercept\\)", "intercept", term),
         term = gsub("healthunhealthy", "food type", term),
         term = gsub("bid_c", "bid", term),
         term = gsub(":bid", " x bid", term)) %>%
  select(sample, type, term, df, `Mdiff [95% CI]`) %>%
  rename("Sample" = sample,
         "Signature Type" = type) %>%
  kable(format = "pandoc", digits = 2)

# complete validation, liked only
data %>%
  filter(algorithm == "regulate > baseline") %>%
  filter(sample == "complete validation") %>%
  filter(liking == "liked") %>%
  group_by(subjectID, type) %>%
  mutate(bid_c = bid - mean(bid, na.rm = TRUE)) %>%
  ungroup() %>%
  nest(-c(sample, type)) %>%
  mutate(
    test = map(data, fit_mod),
    tidied = map(test, broom.mixed::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE) %>%
  filter(effect == "fixed")  %>%
  mutate(`Mdiff [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, estimate - (1.96 * std.error), estimate + (1.96 * std.error)),
         term = gsub("\\(Intercept\\)", "intercept", term),
         term = gsub("healthunhealthy", "food type", term),
         term = gsub("bid_c", "bid", term),
         term = gsub(":bid", " x bid", term)) %>%
  select(sample, type, term, df, `Mdiff [95% CI]`) %>%
  rename("Sample" = sample,
         "Signature Type" = type) %>%
  kable(format = "pandoc", digits = 2)
```

# individual diffs
```{r, fig.width=12, fig.height=8}
ind.liked = data %>%
  filter(sample == "complete validation") %>%
  filter(liking == "liked") %>%
  group_by(subjectID, algorithm, health) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanBid = mean(bid, na.rm = TRUE),
         sample = "complete validation liked only",
         type = ifelse(grepl("logistic", algorithm), "multivariate", "univariate")) %>%
  select(sample, subjectID, algorithm, type, meanPEV, meanBid, health) %>%
  unique()

plot.PEV = data %>%
  group_by(subjectID, algorithm, health) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanBid = mean(bid, na.rm = TRUE)) %>%
  select(sample, subjectID, algorithm,type,  meanPEV, meanBid, health) %>%
  unique() %>%
  bind_rows(ind.liked) %>%
  mutate(sample = factor(sample, levels = c("partial validation", "complete validation", "complete validation liked only"))) %>%
  ggplot(aes(meanPEV, meanBid, color = health)) + 
    geom_point(alpha = .1) +
    geom_smooth(method = "lm", alpha = .2) +
    facet_grid(sample~type + algorithm, scales = "free_x") +
    scale_color_manual(name = "", values = food) +
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    scale_x_continuous(breaks = scales::pretty_breaks(3)) +
    labs(x = "\nmean standardized regulation PEV", y = "mean bid value\n") +
    dc_bw +
    theme(legend.position = "top",
          legend.box = "vertical")

outliers = data %>%
  filter((subjectID == "CHIVES1021" & algorithm == "regulate > baseline" & health == "healthy") | 
         (subjectID == "DEV037" & algorithm == "regulate > baseline" & health == "healthy")) %>%
  group_by(subjectID, algorithm, health) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanBid = mean(bid, na.rm = TRUE),
         regulation = ifelse(dotSTD > 0, 1, 0),
         sumReg = sum(regulation, na.rm = TRUE),
         n = n(), 
         percentReg = (sumReg / n) * 100,
         type = ifelse(grepl("logistic", algorithm), "multivariate", "univariate")) %>%
  select(sample, subjectID, algorithm, type, meanPEV, meanBid, percentReg, health) %>%
  unique() 

ind.liked = data %>%
  filter(!(subjectID == "DEV037" & algorithm == "regulate > baseline" & health == "healthy")) %>%
  filter(sample == "complete validation") %>%
  filter(liking == "liked") %>%
  group_by(subjectID, algorithm, health) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanBid = mean(bid, na.rm = TRUE),
         regulation = ifelse(dotSTD > 0, 1, 0),
         sumReg = sum(regulation, na.rm = TRUE),
         n = n(), 
         percentReg = (sumReg / n) * 100,
         sample = "complete validation liked only",
         type = ifelse(grepl("logistic", algorithm), "multivariate", "univariate")) %>%
  select(sample, subjectID, algorithm, type, meanPEV, meanBid, percentReg, health) %>%
  unique()
  
plot.percent = data %>%
  filter(!((subjectID == "CHIVES1021" & algorithm == "regulate > baseline" & health == "healthy") |
         (subjectID == "DEV037" & algorithm == "regulate > baseline" & health == "healthy"))) %>%
  group_by(subjectID, algorithm, health) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanBid = mean(bid, na.rm = TRUE),
         regulation = ifelse(dotSTD > 0, 1, 0),
         sumReg = sum(regulation, na.rm = TRUE),
         n = n(), 
         percentReg = (sumReg / n) * 100) %>%
  select(sample, subjectID, algorithm, type, meanPEV, meanBid, percentReg, health) %>%
  unique() %>%
  bind_rows(ind.liked) %>%
  mutate(sample = factor(sample, levels = c("partial validation", "complete validation", "complete validation liked only"))) %>%
  ggplot(aes(percentReg, meanBid, color = health)) + 
    geom_point(alpha = .1) +
    geom_point(data = outliers, color = "black", alpha = .2) +
    geom_smooth(method = "lm", alpha = .2) +
    facet_grid(sample~type + algorithm, scales = "free_x") +
    scale_color_manual(name = "", values = food) +
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    scale_x_continuous(breaks = scales::pretty_breaks(3)) +
    labs(x = "\npercent regulation (PEV > 0)", y = "mean bid value\n") +
    dc_bw +
    theme(legend.position = "top",
          legend.box = "vertical")

plot_grid(plot.PEV, plot.percent, ncol = 2, labels = c('A', 'B'))
```

# correlations
```{r, fig.width=14, fig.height=13}
cors.diffs.baseline = data %>%
  group_by(subjectID, algorithm, health) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanBid = mean(bid, na.rm = TRUE),
         regulation = ifelse(dotSTD > 0, 1, 0),
         sumReg = sum(regulation, na.rm = TRUE),
         n = n(), 
         percentReg = (sumReg / n) * 100,
         health1 = health,
         health2 = health) %>%
  select(subjectID, algorithm, type, meanPEV, meanBid, percentReg, health, health1, health2) %>%
  unique() %>%
  spread(health, meanBid) %>%
  group_by(subjectID, algorithm) %>%
  fill(everything(), .direction = "down") %>%
  fill(everything(), .direction = "up") %>%
  mutate(pref.health = healthy - unhealthy) %>%
  spread(health1, meanPEV) %>%
  fill(everything(), .direction = "down") %>%
  fill(everything(), .direction = "up") %>%
  mutate(diff = unhealthy - healthy) %>%
  spread(health2, percentReg) %>%
  fill(everything(), .direction = "down") %>%
  fill(everything(), .direction = "up") %>%
  mutate(diffReg = unhealthy - healthy)

cors.all.data = data %>%
  group_by(subjectID, algorithm, health) %>%
  mutate(`mean PEV` = mean(dotSTD, na.rm = TRUE),
         `mean bid` = mean(bid, na.rm = TRUE),
         regulation = ifelse(dotSTD > 0, 1, 0),
         sumReg = sum(regulation, na.rm = TRUE),
         n = n(), 
         `percent regulation` = (sumReg / n) * 100) %>%
  left_join(., cors.diffs.baseline) %>%
  gather(variable, value, `mean PEV`, `mean bid`, `percent regulation`, pref.health,  diff) %>%
  select(sample, subjectID, health, algorithm, type, variable, value) %>%
  unique() %>%
  filter(!((subjectID == "CHIVES1021" & algorithm == "regulate > baseline" & health == "healthy" & variable == "percent regulation") |
         (subjectID == "DEV037" & algorithm == "regulate > baseline" & health == "healthy" & variable == "percent regulation"))) %>%
  unite("health", c("variable", "health"), sep = " ") %>%
  filter(!health %in% c("pref.health healthy", "diff healthy")) %>%
  mutate(health = ifelse(health == "pref.health unhealthy", "bid difference\n(healthy - unhealthy)",
                       ifelse(health == "diff unhealthy", "PEV difference\n(unhealthy - healthy)", health))) %>%
  ungroup() %>%
  select(sample, subjectID, algorithm, type, health, value)

cors.all.baseline = cors.all.data %>%
  group_by(sample, algorithm, type) %>%
  do({
    health.spread = spread(., health, value)
    cors = cor(health.spread[,-c(1:4)], use = "pairwise.complete.obs") %>%
      as.data.frame() %>%
      mutate(algorithm = health.spread$algorithm[[1]],
             sample = health.spread$sample[[1]],
             health = colnames(health.spread)[-c(1:4)])
  })

cors.liked.baseline = data %>%
  filter(sample == "complete validation") %>%
  filter(liking == "liked") %>%
  group_by(subjectID, algorithm, health) %>%
  mutate(`mean PEV` = mean(dotSTD, na.rm = TRUE),
         `mean bid` = mean(bid, na.rm = TRUE),
         regulation = ifelse(dotSTD > 0, 1, 0),
         sumReg = sum(regulation, na.rm = TRUE),
         n = n(), 
         `percent regulation` = (sumReg / n) * 100) %>%
  left_join(., cors.diffs.baseline) %>%
  gather(variable, value, `mean PEV`, `mean bid`, `percent regulation`, pref.health,  diff) %>%
  select(sample, subjectID, health, algorithm, type, variable, value) %>%
  unique() %>%
  filter(!(subjectID == "DEV037" & algorithm == "regulate > baseline" & health == "healthy" & variable == "percent regulation")) %>%
  unite("health", c("variable", "health"), sep = " ") %>%
  filter(!health %in% c("pref.health healthy", "diff healthy")) %>%
  mutate(health = ifelse(health == "pref.health unhealthy", "bid difference\n(healthy - unhealthy)",
                       ifelse(health == "diff unhealthy", "PEV difference\n(unhealthy - healthy)", health))) %>%
  ungroup() %>%
  select(sample, subjectID, algorithm, type, health, value) %>%
  group_by(sample, algorithm, type) %>%
  do({
    health.spread = spread(., health, value)
    cors = cor(health.spread[,-c(1:4)], use = "pairwise.complete.obs") %>%
      as.data.frame() %>%
      mutate(algorithm = health.spread$algorithm[[1]],
             sample = health.spread$sample[[1]],
             health = colnames(health.spread)[-c(1:4)])
  }) %>%
  ungroup() %>%
  mutate(sample = "complete validation liked only")

cors.all.baseline %>%
  bind_rows(., cors.liked.baseline) %>%
  reshape2::melt() %>%
  mutate(sample = factor(sample, levels = c("partial validation", "complete validation", "complete validation liked only")),
         order = ifelse(grepl("^bid|^PEV", variable), 3,
                 ifelse(grepl("mean", variable), 1,
                 ifelse(grepl("percent", variable), 2, NA))),
         orderHealth = ifelse(grepl("^bid|^PEV", health), 3,
                       ifelse(grepl("mean", health), 1, 
                       ifelse(grepl("percent", health), 2, NA)))) %>%
  ggplot(aes(reorder(health, orderHealth), reorder(variable, order), fill = value)) +
    geom_tile(color = "white") +
    scale_fill_gradientn(name = "", colors = c("#3B9AB2", "white", "#F21A00"), limits = c(-1, 1), breaks = c(-1, 0, 1)) + 
    geom_text(aes(label = round(value, 2)), size = 3, family = "Futura Medium") +
    facet_grid(sample~type + algorithm) +
    labs(x = "", y = "") + 
    dc_bw +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          axis.line = element_blank(),
          legend.position = "none")
```

# specification curve analysis
## partial validation
```{r}
# set na.action for dredge
options(na.action = "na.fail")

# tidy data
data.sca = data %>%
  filter(sample == "partial validation") %>%
  select(subjectID, trial, algorithm, dotSTD, bid, health) %>%
  spread(algorithm, dotSTD) %>%
  na.omit()

# ICC
model.icc = anova(lm(bid ~ subjectID, data = data.sca))
model.icc$`Sum Sq`[1] / sum(model.icc$`Sum Sq`)

# run full model
models = lmer(bid ~ health*`logistic classifier` + health*`regulate > look` + health*`regulate > baseline` + (1 | subjectID), data = data.sca)

# run all possible nested models
models.sca = dredge(models, rank = "AIC", extra = "BIC") %>%
  select(AIC, delta, BIC, df, logLik, weight, `(Intercept)`, health, everything())

# set AIC for null model you want to compare model AIC values to
null = models.sca %>%
  arrange(df) %>%
  filter(health == "+" & df == 4)

# tidy for plotting
plot.data = models.sca %>%
  arrange(AIC) %>%
  mutate(specification = row_number(),
         better.fit = ifelse(AIC == null$AIC, "equal",
                      ifelse(AIC < null$AIC, "yes", "no")))

order = plot.data %>%
  gather(variable, value, -c(AIC, delta, BIC, df, logLik, weight, specification, better.fit)) %>%
  mutate(order = ifelse(grepl("Intercept", variable), 4,
                 ifelse(grepl("health$", variable), 3,
                 ifelse(grepl("health:", variable), 1, 2)))) %>%
  select(variable, order) %>%
  unique()

# variables included in model
variable.names = names(select(plot.data, -starts_with("better"), -specification, -AIC, -BIC, -df, -logLik, -delta, -weight))

# plot top panel
a = plot.data %>%
  ggplot(aes(specification, AIC, color = better.fit)) +
    geom_point(shape = "|", size = 4, alpha = .75) +
    geom_hline(yintercept = null$AIC, linetype = "dashed", color = "#5BBCD6") +
    scale_color_manual(values = c("#5BBCD6", "black", "#F43C13")) +
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    labs(x = "", y = "AIC\n") +
    dc_bw +
    theme(legend.position = "none")

# set plotting order for variables based on number of times it's included in better fitting models
b = plot.data %>%
  gather(variable, value, eval(variable.names)) %>%
  left_join(., order, by = "variable") %>%
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = gsub("\\(Intercept\\)", "intercept", variable),
         variable = gsub("`regulate > look`", "regulate > look", variable),
         variable = gsub("`regulate > baseline`", "regulate > baseline", variable),
         variable = gsub("`logistic classifier`", "logistic classifier", variable),
         variable = gsub("regulate > look:health", "health:regulate > look", variable),
         variable = gsub("regulate > baseline:health", "health:regulate > baseline", variable),
         variable = gsub("logistic classifier:health", "health:logistic classifier", variable),
         variable = gsub("health:", "health  x  ", variable),
         variable = gsub("health", "food type", variable)) %>%
  ggplot(aes(specification, reorder(variable, order), color = better.fit)) +
    geom_text(aes(label = value), alpha = .75) +
    scale_color_manual(values = c("#5BBCD6", "black", "#F43C13")) +
    labs(x = "\nspecification number", y = "variables\n") +
    dc_bw +
    theme(legend.position = "none")

plot.partial = plot_grid(a, b, ncol = 1, align = "v")

# summarize number of better fitting models
plot.data %>%
  gather(variable, value, -c(AIC, delta, BIC, df, logLik, weight, specification, better.fit)) %>%
  mutate(better.fit = ifelse(better.fit == "yes", 1, 0),
         var.better = ifelse(better.fit == 1 & !is.na(value), 1, 0),
         variable = gsub("\\(Intercept\\)", "intercept", variable),
         variable = gsub("`regulate > look`", "regulate > look", variable),
         variable = gsub("`regulate > baseline`", "regulate > baseline", variable),
         variable = gsub("`logistic classifier`", "logistic classifier", variable),
         variable = gsub("regulate > look:health", "health:regulate > look", variable),
         variable = gsub("regulate > baseline:health", "health:regulate > baseline", variable),
         variable = gsub("logistic classifier:health", "health:logistic classifier", variable),
         variable = gsub("health:", "health  x  ", variable),
         variable = gsub("health", "food type", variable)) %>%
  group_by(variable) %>%
  summarize(sum.var = sum(var.better, na.rm = TRUE),
            sum.all = sum(better.fit, na.rm = TRUE),
            percent = (sum.var / sum.all) * 100) %>%
  kable(format = "pandoc", digits = 2)
```

## complete validation
```{r}
# set na.action for dredge
options(na.action = "na.fail")

# tidy data
data.sca = data %>%
  filter(sample == "complete validation") %>%
  select(subjectID, trial, algorithm, dotSTD, bid, health) %>%
  spread(algorithm, dotSTD) %>%
  na.omit()

# ICC
model.icc = anova(lm(bid ~ subjectID, data = data.sca))
model.icc$`Sum Sq`[1] / sum(model.icc$`Sum Sq`)

# run full model
models = lmer(bid ~ health*`logistic classifier` + health*`regulate > look` + health*`regulate > baseline` + (1 | subjectID), data = data.sca)

# run all possible nested models
models.sca = dredge(models, rank = "AIC", extra = "BIC") %>%
  select(AIC, delta, BIC, df, logLik, weight, `(Intercept)`, health, everything())

# set AIC for null model you want to compare model AIC values to
null = models.sca %>%
  arrange(df) %>%
  filter(health == "+" & df == 4)

# tidy for plotting
plot.data = models.sca %>%
  arrange(AIC) %>%
  mutate(specification = row_number(),
         better.fit = ifelse(AIC == null$AIC, "equal",
                      ifelse(AIC < null$AIC, "yes", "no")))

order = plot.data %>%
  gather(variable, value, -c(AIC, delta, BIC, df, logLik, weight, specification, better.fit)) %>%
  mutate(order = ifelse(grepl("Intercept", variable), 4,
                 ifelse(grepl("health$", variable), 3,
                 ifelse(grepl("health:", variable), 1, 2)))) %>%
  select(variable, order) %>%
  unique()

# variables included in model
variable.names = names(select(plot.data, -starts_with("better"), -specification, -AIC, -BIC, -df, -logLik, -delta, -weight))

# plot top panel
a = plot.data %>%
  ggplot(aes(specification, AIC, color = better.fit)) +
    geom_point(shape = "|", size = 4, alpha = .75) +
    geom_hline(yintercept = null$AIC, linetype = "dashed", color = "#5BBCD6") +
    scale_color_manual(values = c("#5BBCD6", "black", "#F43C13")) +
    labs(x = "", y = "") +
    dc_bw +
    theme(legend.position = "none")

# set plotting order for variables based on number of times it's included in better fitting models
b = plot.data %>%
  gather(variable, value, eval(variable.names)) %>%
  left_join(., order, by = "variable") %>%
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = gsub("\\(Intercept\\)", "intercept", variable),
         variable = gsub("`regulate > look`", "regulate > look", variable),
         variable = gsub("`regulate > baseline`", "regulate > baseline", variable),
         variable = gsub("`logistic classifier`", "logistic classifier", variable),
         variable = gsub("regulate > look:health", "health:regulate > look", variable),
         variable = gsub("regulate > baseline:health", "health:regulate > baseline", variable),
         variable = gsub("logistic classifier:health", "health:logistic classifier", variable),
         variable = gsub("health:", "health  x  ", variable),
         variable = gsub("health", "food type", variable)) %>%
  ggplot(aes(specification, reorder(variable, order), color = better.fit)) +
    geom_text(aes(label = value), alpha = .75) +
    scale_color_manual(values = c("#5BBCD6", "black", "#F43C13")) +
    labs(x = "\nspecification number", y = "") +
    dc_bw +
    theme(legend.position = "none",
          axis.text.y = element_blank())

plot.complete = plot_grid(a, b, ncol = 1, align = "v")

# summarize number of better fitting models
plot.data %>%
  gather(variable, value, -c(AIC, delta, BIC, df, logLik, weight, specification, better.fit)) %>%
  mutate(better.fit = ifelse(better.fit == "yes", 1, 0),
         var.better = ifelse(better.fit == 1 & !is.na(value), 1, 0),
         variable = gsub("\\(Intercept\\)", "intercept", variable),
         variable = gsub("`regulate > look`", "regulate > look", variable),
         variable = gsub("`regulate > baseline`", "regulate > baseline", variable),
         variable = gsub("`logistic classifier`", "logistic classifier", variable),
         variable = gsub("regulate > look:health", "health:regulate > look", variable),
         variable = gsub("regulate > baseline:health", "health:regulate > baseline", variable),
         variable = gsub("logistic classifier:health", "health:logistic classifier", variable),
         variable = gsub("health:", "health  x  ", variable),
         variable = gsub("health", "food type", variable)) %>%
  group_by(variable) %>%
  summarize(sum.var = sum(var.better, na.rm = TRUE),
            sum.all = sum(better.fit, na.rm = TRUE),
            percent = (sum.var / sum.all) * 100) %>%
  kable(format = "pandoc", digits = 2)
```

## combined plot
```{r, fig.width = 10, fig.height = 4}
plot_grid(plot.partial, plot.complete, ncol = 2, align = "v", labels = c('A', 'B'), rel_widths = c(.57, .43))
```

# associations with demographics
```{r}
demo = read.csv("../demographics/demographics.csv") %>%
  filter(!is.na(validation))

demo.spread = cors.all.data %>%
  left_join(., demo) %>%
  ungroup() %>%
  mutate(health = gsub("\n", " ", health)) %>%
  spread(health, value)
```

## sex differences
```{r}
demo.uni = demo.spread %>%
  filter(algorithm == "regulate > baseline")

demo.uni %>%
  select_if(is.numeric) %>%
  map_df(~ broom::tidy(t.test(.x ~ demo.uni$sex, na.action = "na.omit")), .id = "x") %>%
  mutate(type = "univariate",
         y = "sex") %>%
  select(type, y, everything()) %>%
  mutate(type = ifelse(x %in% c("age", "BMI", "mean bid healthy", "mean bid unhealthy", "bid difference (healthy - unhealthy)"), "--", type)) %>%
  unique() %>%
  rename("Signature Type" = type,
         "Variable 1" = y,
         "Variable 2" = x,
         "Mfemales" = estimate1,
         "Mmales" = estimate2) %>%
  mutate(`Mdiff [95% CI]`= sprintf("%.02f [%.02f, %.02f]", estimate, conf.low, conf.high)) %>%
  select(`Signature Type`, `Variable 1`, `Variable 2`, `Mdiff [95% CI]`, Mfemales, Mmales) %>%
  arrange(`Signature Type`) %>%
  kable(format = "pandoc", digits = 2)
```

## correlations among variables
```{r}
cor_fun = function(data) pmap(var.names, ~ cor.test(data[[.x]], data[[.y]])) %>% 
  map_df(broom::tidy) %>% 
  cbind(var.names, .)

var.names = tidystringdist::tidy_comb_all(names(select(demo.spread, -c(subjectID, sample, algorithm, type, sex, race.ethnicity, neural.signature, validation)))) %>%
  filter(V1 %in% c("age", "BMI"))

demo.spread %>%
  filter(algorithm == "regulate > baseline") %>%
  nest(-c(type)) %>%
  mutate(
    test = map(data, cor_fun)
  ) %>% 
  unnest(test, .drop = TRUE) %>%
  mutate_if(is.numeric, round, 2) %>%
  mutate(r = sprintf("%.02f [%.02f, %.02f]", estimate, conf.low, conf.high),
         type = ifelse(V2 %in% c("bid difference (healthy - unhealthy)", "mean bid unhealthy", "mean bid healthy", "BMI"), "--", type)) %>%
  select(type, V1, V2, r) %>%
  #filter(V1 %in% c("age", "sex", "BMI")) %>%
  rename("Signature Type" = type,
       "Variable 1" = V1,
       "Variable 2" = V2) %>%
  unique() %>%
  arrange(`Signature Type`) %>%
  kable(format = "pandoc")
```

## associations with sex, age, and BMI
```{r, fig.width = 12, fig.height = 12}
a = demo.spread %>%
  filter(algorithm == "regulate > baseline") %>%
  filter(!is.na(sex)) %>%
  gather(variable, value, -c(subjectID, sample, algorithm, type, sex, race.ethnicity, neural.signature, validation)) %>%
  mutate(type = ifelse(variable %in% c("age", "BMI", "mean bid healthy", "mean bid unhealthy", "bid difference (healthy - unhealthy)"), "", type),
         algorithm = ifelse(variable %in% c("age", "BMI", "mean bid healthy", "mean bid unhealthy", "bid difference (healthy - unhealthy)"), "", algorithm),
         variable = gsub("difference", "difference\n", variable),
         variable = gsub("regulation", "regulation\n", variable),
         variable = factor(variable, levels = c("age", "BMI", "mean bid healthy", "mean bid unhealthy", "bid difference\n (healthy - unhealthy)", "mean PEV healthy", "mean PEV unhealthy", "percent regulation\n healthy", "percent regulation\n unhealthy", "PEV difference\n (unhealthy - healthy)"))) %>%
  unique() %>%
  group_by(type, variable, sex) %>%
  mutate(mean = mean(value, na.rm = TRUE)) %>%
  ggplot(aes(value, fill = sex)) +
    geom_density(color = NA, alpha = .7) +
    geom_vline(aes(xintercept = mean, color = sex), alpha = 1) +
    facet_wrap(~type + variable, scales = "free", ncol = 5,
               labeller = function(labels) {
               labels <- lapply(labels, as.character)
               list(do.call(paste, c(labels, list(sep = "\n"))))
             }) +
    scale_fill_manual(name = "", values = c("#2A5C8C", "#5BBCD6")) + 
    scale_color_manual(name = "", values = c("#2A5C8C", "#5BBCD6")) + 
    scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks(3)) +
    scale_x_continuous(breaks = scales::pretty_breaks(3), expand = expand_scale(mult = c(.05, .04))) +
    labs(x = "\nvalue", y = "density\n") + 
    dc_bw +
    theme(legend.position = "top")

b = demo.spread %>%
  filter(algorithm == "regulate > baseline") %>%
  gather(variable, value, -c(subjectID, sample, algorithm, type, sex, BMI, race.ethnicity, neural.signature, validation)) %>%
  mutate(type = ifelse(variable %in% c("age", "BMI", "mean bid healthy", "mean bid unhealthy", "bid difference (healthy - unhealthy)"), "none", type),
         algorithm = ifelse(variable %in% c("age", "BMI", "mean bid healthy", "mean bid unhealthy", "bid difference (healthy - unhealthy)"), "none", algorithm),
         variable = gsub("difference", "difference\n", variable),
         variable = gsub("regulation", "regulation\n", variable),
         variable = factor(variable, levels = c("age", "BMI", "mean bid healthy", "mean bid unhealthy", "bid difference\n (healthy - unhealthy)", "mean PEV healthy", "mean PEV unhealthy", "percent regulation\n healthy", "percent regulation\n unhealthy", "PEV difference\n (unhealthy - healthy)"))) %>%
  unique() %>%
  ggplot(aes(BMI, value, color = type, fill = type)) +
    geom_point(alpha = .1) +
    geom_smooth(method = "lm", alpha = .2) +
    facet_wrap(~variable, scales = "free", ncol = 3) + 
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    scale_color_manual(name = "", values = c("grey50", algorithm[2])) +
    scale_fill_manual(name = "", values = c("grey50", algorithm[2])) +
    scale_size(name = "", range = c(.5,4)) +
    labs(y = "value\n", x = "\nBMI") + 
    dc_bw +
    theme(legend.position = "top",
          legend.box = "vertical",
          text = element_text(size = 12))

c = demo.spread %>%
  filter(algorithm == "regulate > baseline") %>%
  gather(variable, value, -c(subjectID, sample, algorithm, type, sex, age, race.ethnicity, neural.signature, validation)) %>%
  mutate(type = ifelse(variable %in% c("age", "BMI", "mean bid healthy", "mean bid unhealthy", "bid difference (healthy - unhealthy)"), "none", type),
         algorithm = ifelse(variable %in% c("age", "BMI", "mean bid healthy", "mean bid unhealthy", "bid difference (healthy - unhealthy)"), "none", algorithm),
         variable = gsub("difference", "difference\n", variable),
         variable = gsub("regulation", "regulation\n", variable),
         variable = factor(variable, levels = c("age", "BMI", "mean bid healthy", "mean bid unhealthy", "bid difference\n (healthy - unhealthy)", "mean PEV healthy", "mean PEV unhealthy", "percent regulation\n healthy", "percent regulation\n unhealthy", "PEV difference\n (unhealthy - healthy)"))) %>%
  unique() %>%
  ggplot(aes(age, value, color = type, fill = type)) +
    geom_point(alpha = .1) +
    geom_smooth(method = "lm", alpha = .2) +
    facet_wrap(~variable, scales = "free", ncol = 3) + 
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    scale_color_manual(name = "", values = c("grey50", algorithm[2])) +
    scale_fill_manual(name = "", values = c("grey50", algorithm[2])) +
    scale_size(name = "", range = c(.5,4)) +
    labs(y = "value\n", x = "\nage") + 
    dc_bw +
    theme(legend.position = "top",
          legend.box = "vertical",
          text = element_text(size = 12))

bottom_row = plot_grid(b, c, labels = c('B', 'C'), align = 'h', rel_widths = c(1, 1))
plot_grid(a, bottom_row, labels = c('A', ''), ncol = 1, rel_heights = c(1, 1))
```
