---
title: "Prep WTP Validation Sample Data"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen = 999)
```

# load packages
```{r}
library(tidyverse)
```

# load and tidy task data
```{r}
task = read.csv("~/Documents/code/sanlab/DEV_scripts/fMRI/fx/multiconds/WTP/betaseries/events.csv", stringsAsFactors = FALSE) %>%
  mutate(bid = ifelse(bid == "NULL", NA, bid),
         bid = as.integer(bid),
         health = as.factor(health),
         liking = as.factor(liking)) %>%
  group_by(subjectID, wave, run) %>%
  mutate(trial = row_number()) %>%
  filter(wave == 1)
```

# check responses
Check if wrong buttons were used (i.e., not 5-8)

* DEV002 = exclude; behavioral pilot only, no MRI
* DEV007 = exclude; behavioral pilot only, no MRI
* DEV011 = code normally
* DEV017 = incorrect placement of fingers; recode runs 1-4 (also incorrect in ROC)
* DEV019 = incorrect placement of fingers; recode runs 1-4 (also incorrect in ROC)
* DEV032 = code normally
* DEV033 = incorrect placement of fingers; recode runs 1-3
* DEV054 = exclude; technical error?
* DEV061 = code normally

```{r}
subs = task %>%
  mutate(bid = as.character(bid)) %>%
  group_by(subjectID, run, bid) %>%
  summarize(n = n()) %>%
  spread(bid, n) %>%
  mutate(messed = ifelse(!is.na(`2`), "yes", NA),
         messed = ifelse(is.na(`5`) & !is.na(`<NA>`), "yes", messed)) %>%
  filter(messed == "yes") %>% 
  ungroup() %>% 
  select(subjectID) %>% 
  unique()

task %>%
  mutate(bid = as.character(bid)) %>%
  group_by(subjectID, run, bid) %>%
  summarize(n = n()) %>%
  spread(bid, n) %>%
  mutate(messed = ifelse(!is.na(`2`), "yes", NA),
         messed = ifelse(is.na(`5`) & !is.na(`<NA>`), "yes", messed)) %>%
  filter(subjectID %in% subs$subjectID)
```

# recode and exclude
Recoding  
* DEV017: recode runs1-4, but if liking rating < 3, leave as missing
* DEV019: recode runs1-4, but if liking rating < 3, leave as missing
* DEV033: recode runs1-3, but if liking rating < 3, leave as missing
```{r}
data.ex = task %>%
  mutate(bid = ifelse(subjectID == "DEV033" & !run == "run4", bid - 1, bid),
         bid = ifelse(subjectID == "DEV033" & !run == "run4" & is.na(bid) & liking_rating > 2, 8, bid),
         bid = ifelse(subjectID %in%  c("DEV017", "DEV019"), bid - 1, bid),
         bid = ifelse(subjectID %in%  c("DEV017", "DEV019") & is.na(bid) & liking_rating > 2, 8, bid),
         bid = (bid - 5) / 2) %>%
  group_by(subjectID, wave) %>%
  arrange(subjectID, run) %>%
  mutate(trial = row_number())
```

# load striping info
```{r}
striping = read.csv("striping_QC_validation.csv")
```

# load mean intensity values
```{r}
file_dir = "dotProducts_validation/"
file_pattern = "DEV[0-9]{3}_meanIntensity.txt"
file_list = list.files(file_dir, pattern = file_pattern)

intensities = data.frame()

for (file in file_list) {
  temp = tryCatch(read.table(file.path(file_dir,file), fill = TRUE) %>%
                    rename("subjectID" = V1,
                           "meanIntensity" = V3) %>%
                    extract(V2, "beta", "beta_([0-9]{4}).nii") %>%
                    mutate(beta = as.integer(beta)), error = function(e) message(file))
  intensities = rbind(intensities, temp)
  rm(temp)
}
```

# load dot products
```{r}
file_dir = "dotProducts_validation/"
file_pattern = "DEV[0-9]{3}_dotProducts.txt"
file_list = list.files(file_dir, pattern = file_pattern)

dots = data.frame()

for (file in file_list) {
  temp = tryCatch(read.table(file.path(file_dir,file), fill = TRUE) %>%
                    rename("subjectID" = V1,
                           "map" = V3,
                           "dotProduct" = V4) %>%
                    extract(V2, "beta", "beta_([0-9]{4}).nii") %>%
                    extract(map, "algorithm", "(.*)_.*.nii") %>%
                    mutate(beta = as.integer(beta)), error = function(e) message(file))
  dots = rbind(dots, temp)
  rm(temp)
}
```

# join intensities and dots
* recode trials with extreme intensities as NA
```{r}
dots.merged = dots %>%
  left_join(., intensities, by = c("subjectID", "beta")) %>%
  group_by(subjectID, algorithm) %>%
  mutate(rownum = row_number())

# plot original
dots.merged %>%
  filter(algorithm == "logistic") %>%
  ggplot(aes(1, meanIntensity)) +
    geom_boxplot()

# assess extreme values and exclude when calculating SDs
dots.merged %>%
  filter(algorithm == "logistic") %>%
  arrange(meanIntensity)

dots.merged %>%
  filter(algorithm == "logistic") %>%
  arrange(-meanIntensity)

# recode outliers as NA
dots.merged = dots.merged %>%
  ungroup() %>%
  mutate(meanIntensity = ifelse(meanIntensity > 1 | meanIntensity < -1, NA, meanIntensity),
         median = median(meanIntensity, na.rm = TRUE),
         sd3 = 3*sd(meanIntensity, na.rm = TRUE),
         outlier = ifelse(meanIntensity > median + sd3 | meanIntensity < median - sd3, "yes", "no"),
         dotProduct = ifelse(outlier == "yes", NA, dotProduct))
  
# plot after
dots.merged %>%
  filter(algorithm == "logistic") %>%
  filter(outlier == "no") %>%
  ggplot(aes(1, meanIntensity)) +
    geom_boxplot()
```

# exclude outliers and standardize
* standardize within algorithm and contrast
```{r}
dots.ex = dots.merged %>%
  group_by(algorithm, subjectID) %>%
  mutate(trial = row_number()) %>%
  left_join(., striping, by = c("subjectID", "beta"))  %>%
  mutate(dotProduct = ifelse(!is.na(striping), NA, dotProduct)) %>%
  filter(!algorithm %in% c("ridge", "svm")) %>%
  group_by(subjectID, algorithm) %>% # standardize within sub and algorithm
  mutate(dotSTD = scale(dotProduct, center = FALSE)) 
```

# merge data
Exclusions

* Didn't scan: DEV002, DEV007
* MRI motion (>10%) and data quality exclusions: DEV011, DEV020, DEV032, DEV047, DEV063, DEV064, DEV067, DEV078
* Button box exclusions: DEV054
* Run exclusions: DEV028 (run1), DEV048 (run3), DEV069 (run1)

```{r}
data = left_join(dots.ex, data.ex, by = c("subjectID", "trial")) %>%
  filter(!subjectID %in% c("DEV002", "DEV007", "DEV011", "DEV020", "DEV032", "DEV047", "DEV063", "DEV064", "DEV067", "DEV078", "DEV054")) %>%
  filter(!(subjectID == "DEV028" & run == "run1") & !(subjectID == "DEV048" & run == "run3") & !(subjectID == "DEV069" & run == "run1")) %>%
  ungroup() %>%
  ungroup() %>%
  mutate(algorithm = ifelse(algorithm == "reg_look", "regulate > look", 
                     ifelse(algorithm == "reg", "regulate > rest", 
                     ifelse(algorithm == "logistic", "logistic classifier", algorithm))),
         liking = ifelse(liking_rating > 2, "liked",
                  ifelse(liking_rating < 3, "disliked", NA)))
```

# save variables
```{r}
saveRDS(data, "FV_far_validation.RDS")
```
