---
title: "Prep CR Validation Sample Data"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen = 999)
```

# load packages
```{r}
library(tidyverse)
```

# load tidied data
```{r}
source("../../CR_analyses/load_data_complete.R")
```

# check ratings
Check if wrong buttons were used (i.e., not 5-8)

* DEV001 = code normally
* DEV011 = code normally
* DEV016 = code normally
* DEV017 = incorrect placement of fingers; recode runs 1-4 (also incorrect in WTP)
* DEV019 = incorrect placement of fingers; recode runs 1-4 (also incorrect in WTP)
* DEV020 = code normally
* DEV022 = code normally
* DEV028 = code normally
* DEV032 = incorrect placement of fingers; recode runs 1-2 (see run sheet)
* DEV037 = exclude; technical error
* DEV054 = exclude; technical error
* DEV060 = code normally; task ended early
* DEV061 = code normally; task ended early
* DEV063 = code normally; task ended early
* DEV069 = incorrect placement of fingers in run1
* DEV075 = code normally
* DEV082 = code normally
* DEV083 = code normally

```{r}
subs = data.all %>%
  group_by(subjectID, run, rating) %>%
  summarize(n = n()) %>%
  spread(rating, n) %>%
  mutate(messed = ifelse(is.na(`5`) & !is.na(`<NA>`), "yes", NA)) %>%
  filter(messed == "yes") %>% 
  ungroup() %>% 
  select(subjectID) %>% 
  unique()

data.all %>%
  group_by(subjectID, run, rating) %>%
  summarize(n = n()) %>%
  spread(rating, n) %>%
  mutate(messed = ifelse(is.na(`5`) & !is.na(`<NA>`), "yes", NA)) %>%
  filter(subjectID %in% subs$subjectID)
```

# recode and exclude
Recoding  
* DEV017: recode runs1-4, but if liking rating < 3, leave as missing
* DEV019: recode runs1-4, but if liking rating < 3, leave as missing
* DEV032: recode runs1-2, but if liking rating < 3, leave as missing
* DEV069: recode run1, but if liking rating < 3, leave as missing

```{r}
data.ex = data.all %>%
  mutate(rating = ifelse(subjectID == "DEV069" & run == "run1", rating - 1, rating),
         rating = ifelse(subjectID == "DEV069" & run == "run1" & is.na(rating) & liking_rating > 2, 8, rating),
         rating = ifelse(subjectID == "DEV032" & run %in% c("run1", "run2"), rating - 1, rating),
         rating = ifelse(subjectID == "DEV032" & run %in% c("run1", "run2") & is.na(rating) & liking_rating > 2, 8, rating),
         rating = ifelse(subjectID %in%  c("DEV017", "DEV019"), rating - 1, rating),
         rating = ifelse(subjectID %in%  c("DEV017", "DEV019") & is.na(rating) & liking_rating > 2, 8, rating),
         rating = rating - 4) %>%
  group_by(subjectID, wave) %>%
  arrange(subjectID, run) %>%
  mutate(trial = row_number())
```

# load striping info
```{r}
striping = read.csv("../../CR_analyses/striping_QC_complete.csv")
```

# load mean intensity values
```{r}
file_dir = "../../CR_analyses/dotProducts_complete_validation/"
file_pattern = "DEV[0-9]{3}_meanIntensity.txt"
file_list = list.files(file_dir, pattern = file_pattern)

intensities = data.frame()

for (file in file_list) {
  temp = tryCatch(read.table(file.path(file_dir,file), fill = TRUE) %>%
                    rename("subjectID" = V1,
                           "meanIntensity" = V3) %>%
                    extract(V2, "beta", "beta_([0-9]{4}).nii") %>%
                    mutate(beta = as.integer(beta)), error = function(e) message(file))
  intensities = rbind(intensities, temp)
  rm(temp)
}
```

# load dot products
```{r}
file_dir = "dotProducts_complete_validation/"
file_pattern = "DEV[0-9]{3}_dotProducts.txt"
file_list = list.files(file_dir, pattern = file_pattern)

dots = data.frame()

for (file in file_list) {
  temp = tryCatch(read.table(file.path(file_dir,file), fill = TRUE) %>%
                    rename("subjectID" = V1,
                           "map" = V3,
                           "dotProduct" = V4) %>%
                    extract(V2, "beta", "beta_([0-9]{4}).nii", remove = FALSE) %>%
                    extract(map, "algorithm", "(.*)_.*.nii", remove = FALSE) %>%
                    mutate(beta = as.integer(beta)), error = function(e) message(file))
  dots = rbind(dots, temp)
  rm(temp)
}
```

# join intensities and dots
* recode trials with extreme intensities as NA
```{r}
dots.merged = dots %>%
  left_join(., intensities, by = c("subjectID", "beta")) %>%
  group_by(subjectID, algorithm) %>%
  mutate(rownum = row_number())

# plot original
dots.merged %>%
  filter(algorithm == "multivariate1") %>%
  ggplot(aes(1, meanIntensity)) +
    geom_boxplot()

# assess extreme values and exclude when calculating SDs
dots.merged %>%
  filter(algorithm == "multivariate1") %>%
  arrange(meanIntensity)

dots.merged %>%
  filter(algorithm == "multivariate1") %>%
  arrange(-meanIntensity)

# recode outliers as NA
dots.merged = dots.merged %>%
  ungroup() %>%
  mutate(meanIntensity = ifelse(meanIntensity > 1 | meanIntensity < -1, NA, meanIntensity),
         median = median(meanIntensity, na.rm = TRUE),
         sd3 = 3*sd(meanIntensity, na.rm = TRUE),
         outlier = ifelse(meanIntensity > median + sd3 | meanIntensity < median - sd3, "yes", "no"),
         dotProduct = ifelse(outlier == "yes", NA, dotProduct))
  
# plot after
dots.merged %>%
  filter(algorithm == "multivariate1") %>%
  filter(outlier == "no") %>%
  ggplot(aes(1, meanIntensity)) +
    geom_boxplot()
```

# recode subs
* DEV022 = run4 has 8 trials
* DEV048 = run4 missing
* DEV060 = run1 has 19 trials; couldn't estimate run1 trial 19, run3 trial 20
* DEV061 = run3 has 19 trials; couldn't estimate run3 trial 19
* DEV063 = run2 has 11 trials
* DEV081 = run2 missing (run1 was run twice)
* DEV082 = run2 has 15 trials; couldn't estimate run1 trial 19, run1 trial 20

```{r}
trial.numbers = data.frame(subjectID = c(rep("DEV060", 79), rep("DEV061", 79), rep("DEV063", 71), rep("DEV081", 80), rep("DEV082", 75)),
                           rownum = c(1:79, 1:79, 1:71, 1:80, 1:75),
                           trial = c(1:19, 21:80, 1:59, 61:80, 1:31, 41:80, 1:20, 41:80, 21:40, 1:35, 41:80))

dots.check = dots.merged %>%
  group_by(subjectID, algorithm) %>%
  mutate(rownum = row_number()) %>%
  left_join(., trial.numbers, by = c("subjectID", "rownum")) %>%
  mutate(trial = ifelse(is.na(trial), rownum, trial),
         dotProduct = ifelse(subjectID == "DEV060" & trial %in% 19:20, NA,
                      ifelse(subjectID == "DEV061" & trial == 59, NA,
                      ifelse(subjectID == "DEV082" & trial %in% 19:20, NA, dotProduct)))) %>%
  select(-rownum) %>%
  left_join(., striping, by = c("subjectID", "beta")) %>%
  mutate(dotProduct = ifelse(!is.na(striping), NA, dotProduct))
```

# exclude outliers and standardize
* standardize within subject and algorithm
```{r}
dots.ex = dots.check %>%
  group_by(subjectID, algorithm) %>% # standardize within sub and algorithm
  mutate(dotSTD = scale(dotProduct, center = FALSE)) 
```

# merge data and exclude subs
Exclusions

* MRI motion (>10%) and data quality exclusions: DEV001, DEV011, DEV020, DEV032, DEV047, DEV055, DEV064, DEV066
* Button box exclusions: DEV037, DEV054
* Run exclusions: DEV029 (run3), DEV042 (run4), DEV067 (run4)

Other
* select only craved trials
```{r}
data = left_join(dots.ex, data.ex, by = c("subjectID", "trial")) %>%
  filter(!subjectID %in% c("DEV011", "DEV020", "DEV032", "DEV047", "DEV055", "DEV064", "DEV066", "DEV037", "DEV054")) %>%
  filter(!(subjectID == "DEV029" & run == "run3") & !(subjectID == "DEV042" & run == "run4") & !(subjectID == "DEV067" & run == "run4")) %>%
  ungroup() %>%
  mutate(algorithm = ifelse(algorithm == "reg_look", "regulate > look", 
                     ifelse(algorithm == "reg", "regulate > rest", 
                     ifelse(algorithm == "logistic", "logistic classifier", algorithm)))) %>%
  filter(craving == "craved")
```

# save variables
```{r}
saveRDS(data, "CR_complete_validation_random.RDS")
```

