---
title: "ROC analyses"
author: "Dani Cosme"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.path = "figs/", dpi = 300, colormodel = "cmyk")
options(scipen = 999)
```

# load packages
```{r}
library(tidyverse)
library(lme4)
library(lmerTest)
library(knitr)
library(MuMIn)
library(cowplot)
library(caret)
library(ROCR)
library(broom)
library(scales)
```

# define color palettes
```{r}
algorithm = c("#006989", "#FEC601", "#F43C13", "#00A5CF", "#00A878")
instruction = wesanderson::wes_palette("Darjeeling1", 2, "continuous")
craving = wesanderson::wes_palette("Darjeeling1", 3, "continuous")
rating = c("#00A08A", "#F2AD00", "#F98400", "#FF0000", "#A80000")
dc_bw = readRDS("~/dc_bw.Rds") +
    theme(text = element_text(size = 13, family = "Futura Medium"))
          # legend.title = element_text(size = 9),
          # legend.text = element_text(size = 8))
```

# load and tidy data
```{r}
dev = readRDS("ROC_near_validation.RDS") %>%
  mutate(sample = "near validation") %>%
  select(sample, subjectID, run, trial, instruction, craving, rating, rt, algorithm, dotProduct, dotSTD)

val = readRDS("ROC_far_validation.RDS") %>%
  mutate(sample = "far validation") %>%
  select(sample, subjectID, run, trial, instruction, craving, rating, rt, algorithm, dotProduct, dotSTD)

data = bind_rows(dev, val) %>%
  arrange(subjectID, trial) %>%
  filter(!is.na(rating)) %>%
  mutate(sample = factor(sample, levels = c("near validation", "far validation")))
```

# descriptives
## number of participants
```{r}
data %>%
  filter(algorithm == "logistic classifier") %>%
  select(sample, subjectID) %>%
  unique() %>%
  group_by(sample) %>%
  summarize(n = n())
```

## ratings
```{r}
data %>%
  filter(algorithm == "logistic classifier") %>%
  group_by(sample, instruction) %>%
  summarize(n = n(),
            mean = round(mean(rating, na.rm = TRUE), 2),
            sd = round(sd(rating, na.rm = TRUE), 2),
            min = min(rating, na.rm = TRUE),
            max = max(rating, na.rm = TRUE))

data %>%
  filter(algorithm == "logistic classifier") %>%
  group_by(sample, instruction) %>%
  summarize(n = n(),
            mean = round(mean(rating, na.rm = TRUE), 2),
            sd = round(sd(rating, na.rm = TRUE), 2)) %>%
  gather(variable, value, mean, sd, n) %>%
  unite(sample, c(sample, variable), sep = " ") %>%
  spread(sample, value) %>%
  kable(format = "pandoc")
```

## pattern expression values
```{r, fig.width=7, fig.height=7}
data %>%
  group_by(sample, algorithm, instruction) %>%
  summarize(n = n(),
            mean = round(mean(dotSTD, na.rm = TRUE), 2),
            sd = round(sd(dotSTD, na.rm = TRUE), 2),
            se = sd / sqrt(n - 1),
            min = min(dotSTD, na.rm = TRUE),
            max = max(dotSTD, na.rm = TRUE))

data %>%
  group_by(sample, algorithm, instruction) %>%
  summarize(n = n(),
            mean = round(mean(dotSTD, na.rm = TRUE), 2),
            sd = round(sd(dotSTD, na.rm = TRUE), 2)) %>%
  gather(variable, value, mean, sd) %>%
  unite(algorithm, c(algorithm, variable), sep = " ") %>%
  spread(algorithm, value) %>%
  group_by(sample, instruction) %>%
  fill(everything(), .direction = "up") %>%
  fill(everything(), .direction = "down") %>%
  unique() %>%
  kable(format = "pandoc")

a = data %>%
  group_by(instruction, sample, algorithm) %>%
  mutate(mean = mean(dotSTD, na.rm = TRUE)) %>%
  ggplot(aes(dotSTD, fill = instruction)) +
    geom_vline(aes(xintercept = mean, color = instruction), alpha = .7) +
    geom_density(color = NA, alpha = .7) +
    facet_grid(sample~algorithm, scales = "free_x") +
    scale_fill_manual(name = "", values = instruction) + 
    scale_color_manual(name = "", values = instruction) + 
    scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks(4)) +
    scale_x_continuous(breaks = scales::pretty_breaks(4)) +
    labs(x = "\nstandardized regulation PEV", y = "density\n") + 
    dc_bw +
    theme(legend.position = c(.74, .915))

b = data %>%
  group_by(algorithm, subjectID, instruction) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE)) %>%
  group_by(instruction, sample, algorithm) %>%
  mutate(mean = mean(meanPEV, na.rm = TRUE)) %>%
  ggplot(aes(meanPEV, fill = instruction)) +
    geom_vline(aes(xintercept = mean, color = instruction), alpha = .7) +
    geom_density(color = NA, alpha = .7) +
    facet_grid(sample~algorithm, scales = "free_x") +
    scale_fill_manual(name = "", values = instruction) + 
    scale_color_manual(name = "", values = instruction) + 
    scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks(3)) +
    scale_x_continuous(breaks = scales::pretty_breaks(3)) +
    labs(x = "\nparticipant mean standardized regulation PEV", y = "density\n") + 
    dc_bw +
    theme(legend.position = "none")

(plot = plot_grid(a, b, ncol = 1, align = "v", labels = c('A', 'B')))

data %>%
  select(sample, subjectID, trial, algorithm, dotSTD) %>%
  spread(algorithm, dotSTD) %>%
  mutate(subjectID = as.factor(subjectID)) %>%
  unique() %>%
  ungroup() %>%
  nest(-c(sample)) %>% 
  mutate(`logistic classifier_regulate > look` = map(data, ~ rmcorr::rmcorr(subjectID, `logistic classifier`, `regulate > look`, .)),
         `regulate > rest_logistic classifier` = map(data, ~ rmcorr::rmcorr(subjectID, `logistic classifier`, `regulate > rest`, .)),
         `regulate > look_regulate > rest` = map(data, ~ rmcorr::rmcorr(subjectID, `regulate > rest`, `regulate > look`, .))) %>%
  gather(test, model, contains("reg")) %>%
  group_by(sample, test) %>%
  mutate(r = sprintf("%s [%s, %s]", round(model[[1]][[1]], 2), round(model[[1]][[4]][1], 2), round(model[[1]][[4]][2], 2)),
         df = model[[1]][[2]],
         p = round(model[[1]][[3]], 3),
         p = ifelse(p == 0, "< .001", as.character(p))) %>%
  ungroup() %>%
  select(sample, test, r, df) %>%
  extract(test, c("var1", "var2"), "(.*)_(.*)") %>%
  spread(var1, r) %>%
  select(sample, var2, df, `regulate > rest`, everything()) %>%
  kable(format = 'pandoc')
```

# accuracy and roc curves
```{r, fig.width=5.5, fig.height=5}
# accuracy
data %>%
  select(sample, subjectID, trial, algorithm, instruction, rating, dotSTD) %>%
  mutate(guess.instruction = ifelse(dotSTD > 0, "regulate", "look"),
         instruction = as.factor(instruction),
         guess.instruction = as.factor(guess.instruction)) %>%
  ungroup() %>%
  nest(-c(sample, algorithm)) %>% 
  mutate(
    test = map(data, ~ confusionMatrix(.$guess.instruction, .$instruction)),
    tidied = map(test, broom::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE)

# table
data %>%
  select(sample, subjectID, trial, algorithm, instruction, rating, dotSTD) %>%
  mutate(guess.instruction = ifelse(dotSTD > 0, "regulate", "look"),
         instruction = as.factor(instruction),
         guess.instruction = as.factor(guess.instruction)) %>%
  ungroup() %>%
  nest(-c(sample, algorithm)) %>% 
  mutate(
    test = map(data, ~ confusionMatrix(.$guess.instruction, .$instruction)),
    tidied = map(test, broom::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE) %>%
  filter(term %in% c("accuracy", "balanced_accuracy", "specificity", "sensitivity")) %>%
  spread(term, estimate) %>%
  group_by(sample, algorithm) %>%
  fill(everything(), .direction = "up") %>%
  fill(everything(), .direction = "down") %>%
  unique() %>%
  rename(`balanced accuracy` = balanced_accuracy,
         "p" = p.value) %>%
  mutate(`balanced accuracy` = round(`balanced accuracy`, 2),
         sensitivity = round(sensitivity, 2),
         specificity = round(specificity, 2),
         accuracy = sprintf('%s [%s, %s]', round(accuracy, 2), round(conf.low, 2), round(conf.high, 2)),
         p = round(p, 3),
         p = ifelse(p == 0, "< .001", as.character(p))) %>%
  select(sample, algorithm, `balanced accuracy`, sensitivity, specificity, accuracy, p) %>%
  kable(format = "pandoc")

# roc curve
data %>%
  mutate(instruction = ifelse(instruction == "regulate", 1, 0)) %>%
  group_by(sample, algorithm) %>%
  do({
    sample = .$sample
    algorithm = .$algorithm
    pred = prediction(.$dotSTD, .$instruction)
    perf = performance(pred, measure = "tpr", x.measure = "fpr")
    data.frame(cut = perf@alpha.values[[1]],fpr = perf@x.values[[1]],tpr = perf@y.values[[1]])
  }) %>%
  ggplot(aes(fpr, tpr, color = algorithm, linetype = sample)) +
    geom_line() +
    geom_abline(intercept = 0, slope = 1) +
    scale_color_manual(name = "", values = algorithm) +
    scale_linetype_manual(name =  "", values = c("dotted", "solid")) +
    labs(x = "\nfalse positive rate (1 - specificity)", y = "true positive rate (sensitivity)\n") +
    dc_bw +
    theme(legend.position = c(.8, .3),
          legend.spacing.y = unit(-.1, "cm"))

data %>%
  filter(algorithm == "logistic classifier") %>%
  mutate(instruction = ifelse(instruction == "regulate", 1, 0)) %>%
  group_by(sample, algorithm) %>%
  do({
    sample = .$sample
    algorithm = .$algorithm
    pred = prediction(.$dotSTD, .$instruction)
    perf = performance(pred, measure = "tpr", x.measure = "fpr")
    data.frame(cut = perf@alpha.values[[1]],fpr = perf@x.values[[1]],tpr = perf@y.values[[1]])
  }) %>%
  ggplot(aes(fpr, tpr, linetype = sample)) +
    geom_line(color = algorithm[1]) +
    geom_abline(intercept = 0, slope = 1) +
    scale_linetype_manual(name =  "", values = c("solid", "dotted")) +
    labs(x = "\nfalse positive rate (1 - specificity)", y = "true positive rate (sensitivity)\n") +
    dc_bw +
    theme(legend.position = c(.8, .15))
```

# visualize
## instruction
```{r}
data %>%
  ggplot(aes(algorithm, dotSTD, fill = instruction)) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    facet_grid(~sample) +
    scale_fill_manual(name = "", values = instruction) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = c(.9, .15))

data %>%
  ggplot(aes(algorithm, dotSTD, fill = instruction, alpha = sample)) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    scale_fill_manual(name = "", values = instruction) + 
    scale_alpha_discrete(name = "", range = c(.6, 1)) +
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = c(.8, .2),
          #legend.spacing.x = unit(0, "cm"),
          legend.box = "horizontal")
  
data %>%
  filter(!is.na(rating)) %>%
  ggplot(aes(instruction, dotSTD)) +
    stat_summary(aes(group = subjectID), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = 1), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = instruction), fun.data = mean_cl_boot,  geom = "pointrange", width = 0) + 
    facet_grid(sample~algorithm) +
    scale_color_manual(name = "", values = instruction) +
    scale_y_continuous(breaks = scales::pretty_breaks(4)) +
    coord_cartesian(ylim = c(-.75, 1.25)) +
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none")

data %>%
  filter(!is.na(rating)) %>%
  ggplot(aes(instruction, dotSTD)) +
    stat_summary(aes(group = subjectID), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = 1), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = instruction), fun.data = mean_cl_boot,  geom = "pointrange") + 
    facet_grid(algorithm~sample, scales = "free_y") +
    scale_color_manual(name = "", values = instruction) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none")
```

```{r, fig.width=7, fig.height=8}
a = data %>%
  ggplot(aes(instruction, dotSTD, fill = instruction, alpha = sample)) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    facet_grid(~algorithm) +
    scale_fill_manual(name = "", values = instruction) + 
    scale_alpha_discrete(name = "", range = c(.6, 1)) +
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = c(.8, .2),
          #legend.spacing.x = unit(0, "cm"),
          legend.box = "horizontal")
  
b = data %>%
  filter(!is.na(rating)) %>%
  ggplot(aes(instruction, dotSTD)) +
    stat_summary(aes(group = subjectID), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = 1), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = instruction), fun.data = mean_cl_boot,  geom = "pointrange", width = 0) + 
    facet_grid(sample~algorithm) +
    scale_color_manual(name = "", values = instruction) +
    coord_cartesian(ylim = c(-1, 1.25)) +
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none")
          #strip.text.y = element_blank())

plot_grid(a, b, ncol = 1, align = "v", labels = c('A', 'B'))
```

## rating
```{r}
data %>%
  ggplot(aes(algorithm, dotSTD, fill = as.factor(rating))) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    scale_fill_manual(name = "", values = rating) + 
    facet_grid(~sample) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw

data %>%
  group_by(sample, rating, algorithm) %>%
  mutate(n.obs = n()) %>%
  ggplot(aes(as.factor(rating), dotSTD, color = algorithm)) +
    stat_summary(aes(group = algorithm), fun.y = mean, geom = "line") +
    stat_summary(fun.data = mean_cl_boot, geom = "linerange") +
    stat_summary(aes(size = n.obs), fun.y = mean, geom = "point") +
    scale_color_manual(name = "", values = algorithm) + 
    scale_size(name = "", range = c(1,5)) + 
    facet_grid(~sample, scales = "free_x") + 
    labs(x = "\nrating", y = "standardized regulation PEV\n") + 
    dc_bw

data %>%
  ggplot(aes(algorithm, dotSTD, fill = as.factor(rating))) +
    stat_summary(fun.y = mean, geom = "bar", position = position_dodge(width = 0.95)) +
    stat_summary(fun.data = mean_cl_boot, geom = "errorbar", position = position_dodge(width = 0.95), width = 0) +
    scale_fill_manual(name = "", values = rating) + 
    facet_grid(sample~instruction) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw

data %>%
  group_by(sample, rating, algorithm, instruction) %>%
  mutate(n.obs = n()) %>%
  ggplot(aes(as.factor(rating), dotSTD, color = algorithm)) +
    stat_summary(aes(group = algorithm), fun.y = mean, geom = "line") +
    stat_summary(fun.data = mean_cl_boot, geom = "linerange") +
    stat_summary(aes(size = n.obs), fun.y = mean, geom = "point") +
    scale_color_manual(name = "", values = algorithm) + 
    scale_size(name = "", range = c(1,5)) + 
    facet_grid(sample~instruction) + 
    labs(x = "\nrating", y = "standardized regulation PEV\n") + 
    dc_bw
```

## rating and instruction
```{r}
data %>%
  group_by(sample, rating, algorithm, instruction) %>%
  mutate(n.obs = n()) %>%
  ggplot(aes(as.factor(rating), dotSTD, color = instruction)) +
    stat_summary(aes(group = instruction), fun.y = mean, geom = "line") +
    stat_summary(fun.data = mean_cl_boot, geom = "linerange") +
    stat_summary(aes(size = n.obs), fun.y = mean, geom = "point") +
    scale_color_manual(name = "", values = instruction) + 
    scale_size(name = "", range = c(1,5)) + 
    facet_grid(sample~algorithm) + 
    labs(x = "\nrating", y = "standardized regulation PEV\n") + 
    dc_bw
```

## rating high v. low
```{r}
data %>%
  mutate(rating.bin = ifelse(sample == "near validation" & rating > 3, "high", 
                      ifelse(sample == "near validation" & rating < 3, "low",
                      ifelse(sample == "far validation" & rating >= 3, "high",
                      ifelse(sample == "far validation" & rating < 3, "low", NA)))),
         rating.bin = factor(rating.bin, levels = c("low", "high"))) %>%
  filter(!is.na(rating.bin)) %>%
  ggplot(aes(rating.bin, dotSTD)) +
    stat_summary(aes(group = subjectID), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = 1), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = rating.bin), fun.data = mean_cl_boot, geom = "pointrange", width = 0) + 
    facet_grid(sample~algorithm) +
    scale_color_manual(name = "", values = craving) + 
    coord_cartesian(ylim = c(-1.25, 1.25)) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none")

data %>%
  mutate(rating.bin = ifelse(sample == "near validation" & rating > 3, "high", 
                      ifelse(sample == "near validation" & rating < 3, "low",
                      ifelse(sample == "far validation" & rating >= 3, "high",
                      ifelse(sample == "far validation" & rating < 3, "low", NA)))),
         rating.bin = factor(rating.bin, levels = c("low", "high"))) %>%
  filter(!is.na(rating.bin)) %>%
  ggplot(aes(rating.bin, dotSTD)) +
    stat_summary(aes(group = interaction(subjectID, instruction), color = instruction), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = instruction, color = instruction), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = instruction), fun.data = mean_cl_boot, geom = "pointrange", width = 0) + 
    facet_grid(sample~algorithm) +
    scale_color_manual(name = "", values = instruction) + 
    coord_cartesian(ylim = c(-1.5, 2)) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = c(.9, .15))
```

## combined
```{r, fig.width=10, fig.height=9}
a = data %>%
  group_by(sample, rating, algorithm) %>%
  mutate(n.obs = n()) %>%
  ggplot(aes(as.factor(rating), dotSTD, color = algorithm)) +
    stat_summary(aes(group = algorithm), fun.y = mean, geom = "line") +
    stat_summary(fun.data = mean_cl_boot, geom = "linerange") +
    stat_summary(aes(size = n.obs), fun.y = mean, geom = "point") +
    scale_color_manual(name = "", values = algorithm) + 
    scale_size(name = "", range = c(.5,3), breaks = c(300, 600, 900)) + 
    facet_grid(~sample, scales = "free_x") + 
    labs(x = "\ncraving rating", y = "standardized regulation PEV\n") + 
    dc_bw

b = data %>%
  mutate(rating.bin = ifelse(sample == "near validation" & rating > 3, "high", 
                      ifelse(sample == "near validation" & rating < 3, "low",
                      ifelse(sample == "far validation" & rating >= 3, "high",
                      ifelse(sample == "far validation" & rating < 3, "low", NA)))),
         rating.bin = factor(rating.bin, levels = c("low", "high"))) %>%
  filter(!is.na(rating.bin)) %>%
  ggplot(aes(rating.bin, dotSTD)) +
    stat_summary(aes(group = subjectID), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = 1), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = rating.bin), fun.data = mean_cl_boot, geom = "pointrange", width = 0) + 
    facet_grid(sample~algorithm) +
    scale_color_manual(name = "", values = craving) + 
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    coord_cartesian(ylim = c(-1.25, 1.75)) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = "none")

c = data %>%
  mutate(rating.bin = ifelse(sample == "near validation" & rating > 3, "high", 
                      ifelse(sample == "near validation" & rating < 3, "low",
                      ifelse(sample == "far validation" & rating >= 3, "high",
                      ifelse(sample == "far validation" & rating < 3, "low", NA)))),
         rating.bin = factor(rating.bin, levels = c("low", "high"))) %>%
  filter(!is.na(rating.bin)) %>%
  ggplot(aes(rating.bin, dotSTD)) +
    stat_summary(aes(group = interaction(subjectID, instruction), color = instruction), fun.y = mean, geom = "line", alpha = .1, size = .5) +
    stat_summary(aes(group = instruction, color = instruction), fun.y = mean, geom = "line", size = .75) +
    stat_summary(aes(color = instruction), fun.data = mean_cl_boot, geom = "pointrange", width = 0) + 
    facet_grid(sample~algorithm) +
    scale_color_manual(name = "", values = instruction) + 
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    coord_cartesian(ylim = c(-1.25, 1.75)) + 
    labs(y = "standardized regulation PEV\n", x = "") + 
    dc_bw +
    theme(legend.position = c(.9, .15))

bottom_row = plot_grid(b, c, labels = c('B', 'C'), align = 'h', rel_widths = c(1, 1))
plot_grid(a, bottom_row, labels = c('A', ''), ncol = 1, rel_heights = c(1, 1))

a = data %>%
  group_by(sample, rating, algorithm) %>%
  mutate(n.obs = n()) %>%
  ggplot(aes(as.factor(rating), dotSTD, color = algorithm)) +
    stat_summary(aes(group = algorithm), fun.y = mean, geom = "line") +
    stat_summary(fun.data = mean_cl_boot, geom = "linerange") +
    stat_summary(aes(size = n.obs), fun.y = mean, geom = "point") +
    scale_color_manual(name = "", values = algorithm) + 
    scale_size(name = "", range = c(.5,3), breaks = c(300, 600, 900)) + 
    facet_grid(sample~., scales = "free_x") + 
    labs(x = "\ncraving rating", y = "standardized regulation PEV\n") + 
    dc_bw +
    theme(legend.position = "top",
          legend.box = "vertical")

bottom_row = plot_grid(b, c, labels = c('B', 'C'), ncol = 1, rel_widths = c(1, 1))
plot_grid(a, bottom_row, labels = c('A', ''), ncol = 2, rel_widths = c(1, 1))
```

# individual diffs
## task
```{r, fig.width=6, fig.height=5}
data %>%
  group_by(subjectID, algorithm, instruction, craving) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE)) %>%
  select(sample, subjectID, algorithm, meanPEV, instruction) %>%
  unique() %>%  
  ggplot(aes(instruction, meanPEV, color = instruction)) + 
    geom_boxplot() +
    facet_grid(algorithm~sample, scales = "free_y") +
    scale_color_manual(values = instruction) +
    labs(x = "", y = "mean standardized regulation PEV\n") +
    dc_bw

outliers = data %>%
  filter((subjectID == "CHIVES1055" & algorithm == "regulate > rest") | (subjectID == "CHIVES1091" & algorithm == "logistic classifier" & instruction == "regulate") | (subjectID == "DEV001" & algorithm == "regulate > rest" & instruction == "regulate")) %>%
  group_by(subjectID, algorithm, instruction) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanRating = mean(rating, na.rm = TRUE)) %>%
  select(sample, subjectID, algorithm, meanPEV, meanRating, instruction) %>%
  unique() 

data %>%
  filter(!((subjectID == "CHIVES1055" & algorithm == "regulate > rest") | (subjectID == "CHIVES1091" & algorithm == "logistic classifier" & instruction == "regulate") | (subjectID == "DEV001" & algorithm == "regulate > rest" & instruction == "regulate"))) %>%
  group_by(subjectID, algorithm, instruction) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanRating = mean(rating, na.rm = TRUE)) %>%
  select(sample, subjectID, algorithm, meanPEV, meanRating, instruction) %>%
  unique() %>%
  ggplot(aes(meanPEV, meanRating)) + 
    geom_point(aes(color = instruction)) +
    geom_point(data = outliers, color = "black") +
    geom_smooth(method = "lm", alpha = .2, color = "black") +
    facet_grid(sample~algorithm, scales = "free_x") +
    scale_color_manual(values = instruction) +
    labs(x = "\nmean standardized regulation PEV", y = "mean craving rating\n") +
    dc_bw

data %>%
  filter(!((subjectID == "CHIVES1055" & algorithm == "regulate > rest") | (subjectID == "CHIVES1091" & algorithm == "logistic classifier" & instruction == "regulate") | (subjectID == "DEV001" & algorithm == "regulate > rest" & instruction == "regulate"))) %>%
  group_by(subjectID, algorithm, instruction) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanRating = mean(rating, na.rm = TRUE)) %>%
  select(sample, subjectID, algorithm, meanPEV, meanRating, instruction) %>%
  unique() %>%
  ungroup() %>%
  nest(-c(sample, algorithm)) %>% 
  mutate(
    test = map(data, ~ cor.test(.x$meanRating, .x$meanPEV)),
    tidied = map(test, broom::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE)

data %>%
  filter(!((subjectID == "CHIVES1055" & algorithm == "regulate > rest") | (subjectID == "CHIVES1091" & algorithm == "logistic classifier" & instruction == "regulate") | (subjectID == "DEV001" & algorithm == "regulate > rest" & instruction == "regulate"))) %>%
  group_by(subjectID, algorithm, instruction) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanRating = mean(rating, na.rm = TRUE)) %>%
  select(sample, subjectID, algorithm, meanPEV, meanRating, instruction) %>%
  unique() %>%
  ggplot(aes(meanPEV, meanRating, color = instruction)) + 
    geom_point(alpha = .2) +
    geom_point(data = outliers, color = "black", alpha = .4) +
    geom_smooth(method = "lm", alpha = .2) +
    facet_grid(sample~algorithm, scales = "free_x") +
    scale_color_manual(name = "", values = instruction) +
    scale_y_continuous(breaks = scales::pretty_breaks(3)) +
    scale_x_continuous(breaks = scales::pretty_breaks(3)) +
    labs(x = "\nmean standardized regulation PEV", y = "mean craving rating\n") +
    dc_bw +
    theme(legend.position = "top",
          legend.box = "vertical")

data %>%
  filter(!((subjectID == "CHIVES1055" & algorithm == "regulate > rest") | (subjectID == "CHIVES1091" & algorithm == "logistic classifier" & instruction == "regulate") | (subjectID == "DEV001" & algorithm == "regulate > rest" & instruction == "regulate"))) %>%
  group_by(subjectID, algorithm, instruction) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanRating = mean(rating, na.rm = TRUE)) %>%
  select(sample, subjectID, algorithm, meanPEV, meanRating, instruction) %>%
  unique() %>%
  ungroup() %>%
  nest(-c(sample, algorithm, instruction)) %>% 
  mutate(
    test = map(data, ~ cor.test(.x$meanRating, .x$meanPEV)),
    tidied = map(test, broom::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE)

data %>%
  filter(!((subjectID == "CHIVES1055" & algorithm == "regulate > rest") | (subjectID == "CHIVES1091" & algorithm == "logistic classifier" & instruction == "regulate") | (subjectID == "DEV001" & algorithm == "regulate > rest" & instruction == "regulate"))) %>%
  group_by(subjectID, algorithm, instruction) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanRating = mean(rating, na.rm = TRUE),
         instruction1 = instruction) %>%
  select(sample, subjectID, algorithm, meanPEV, meanRating, instruction, instruction1) %>%
  unique() %>%
  spread(instruction, meanRating) %>%
  group_by(subjectID, algorithm) %>%
  fill(everything(), .direction = "down") %>%
  fill(everything(), .direction = "up") %>%
  mutate(success = look - regulate,
         success.percent = ((look - regulate) / look) * 100) %>%
  spread(instruction1, meanPEV) %>%
  mutate(diff = regulate - look) %>%
  ggplot(aes(diff, success.percent)) + 
    geom_point() +
    geom_smooth(method = "lm", alpha = .2) +
    facet_grid(sample~algorithm, scales = "free_x") +
    #scale_color_manual(values = instruction) +
    labs(x = "\ndifference in mean regulation PEV (regulate - look)", y = "percent change in craving (look - regulate / look)") +
    dc_bw

data %>%
  filter(!((subjectID == "CHIVES1055" & algorithm == "regulate > rest") | (subjectID == "CHIVES1091" & algorithm == "logistic classifier" & instruction == "regulate") | (subjectID == "DEV001" & algorithm == "regulate > rest" & instruction == "regulate"))) %>%
  filter(!is.na(rating)) %>%
  group_by(subjectID, algorithm, instruction) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanRating = mean(rating, na.rm = TRUE),
         instruction1 = instruction) %>%
  select(sample, subjectID, algorithm, meanPEV, meanRating, instruction, instruction1) %>%
  unique() %>%
  spread(instruction, meanRating) %>%
  group_by(subjectID, algorithm) %>%
  fill(everything(), .direction = "down") %>%
  fill(everything(), .direction = "up") %>%
  mutate(success = look - regulate,
         success.percent = ((look - regulate) / look) * 100) %>%
  spread(instruction1, meanPEV) %>%
  mutate(diff = regulate - look) %>% 
  ungroup() %>%
  nest(-c(sample, algorithm)) %>% 
  mutate(
    test = map(data, ~ cor.test(.x$success.percent, .x$diff)),
    tidied = map(test, broom::tidy)
  ) %>% 
  unnest(tidied, .drop = TRUE)
```

# correlations
```{r, fig.width=13, fig.height=9}
cors.diffs = data %>%
  filter(!((subjectID == "CHIVES1055" & algorithm == "regulate > rest") | (subjectID == "CHIVES1091" & algorithm == "logistic classifier" & instruction == "regulate") | (subjectID == "DEV001" & algorithm == "regulate > rest" & instruction == "regulate"))) %>%
  filter(!is.na(rating)) %>%
  group_by(subjectID, algorithm, instruction) %>%
  mutate(meanPEV = mean(dotSTD, na.rm = TRUE),
         meanRating = mean(rating, na.rm = TRUE),
         instruction1 = instruction) %>%
  select(sample, subjectID, algorithm, meanPEV, meanRating, instruction, instruction1) %>%
  unique() %>%
  spread(instruction, meanRating) %>%
  group_by(subjectID, algorithm) %>%
  fill(everything(), .direction = "down") %>%
  fill(everything(), .direction = "up") %>%
  mutate(success = look - regulate,
         success.percent = ((look - regulate) / look) * 100) %>%
  spread(instruction1, meanPEV) %>%
  mutate(diff = regulate - look)

cors = data %>%
  filter(!((subjectID == "CHIVES1055" & algorithm == "regulate > rest") | (subjectID == "CHIVES1091" & algorithm == "logistic classifier" & instruction == "regulate") | (subjectID == "DEV001" & algorithm == "regulate > rest" & instruction == "regulate"))) %>%
  #filter(!is.na(rating)) %>%
  group_by(subjectID, algorithm, instruction) %>%
  mutate(`mean PEV` = mean(dotSTD, na.rm = TRUE),
         `mean rating` = mean(rating, na.rm = TRUE)) %>%
  left_join(., cors.diffs) %>%
  gather(variable, value, `mean PEV`, `mean rating`, success, success.percent, diff) %>%
  select(sample, subjectID, instruction, algorithm, variable, value) %>%
  unique() %>%
  unite("instruction", c("variable", "instruction"), sep = " ") %>%
  filter(!instruction %in% c("success.percent regulate", "success regulate", "diff regulate")) %>%
  mutate(instruction = ifelse(instruction == "success.percent look", "rating percent change\n(look - regulate / look)",
                    ifelse(instruction == "success look", "rating difference\n(look - regulate)",
                    ifelse(instruction == "diff look", "PEV difference\n(regulate - look)", instruction)))) %>%
  ungroup() %>%
  select(sample, subjectID, algorithm, instruction, value) %>%
  group_by(sample, algorithm) %>%
  do({
    instruction.spread = spread(., instruction, value)
    cors = cor(instruction.spread[,-c(1:3)], use = "pairwise.complete.obs") %>%
      as.data.frame() %>%
      mutate(algorithm = instruction.spread$algorithm[[1]],
             sample = instruction.spread$sample[[1]],
             instruction = colnames(instruction.spread)[-c(1:3)])
  })


cors %>%
  reshape2::melt() %>%
  ggplot(aes(instruction, variable, fill = value)) +
    geom_tile(color = "white") +
    scale_fill_gradientn(name = "", colors = c("#3B9AB2", "white", "#F21A00"), limits = c(-1, 1), breaks = c(-1, 0, 1)) + 
    geom_text(aes(label = round(value, 2)), size = 3, family = "Futura Medium") +
    facet_grid(sample~algorithm) +
    labs(x = "", y = "") + 
    dc_bw +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
          axis.line = element_blank(),
          legend.position = "none")
```

# specification curve analysis
## near validation subsample
```{r}
# set na.action for dredge
options(na.action = "na.fail")

# tidy data
data.sca = data %>%
  filter(sample == "near validation") %>%
  select(subjectID, trial, algorithm, dotSTD, rating, instruction) %>%
  spread(algorithm, dotSTD) %>%
  na.omit()

# ICC
model.icc = anova(lm(rating ~ subjectID, data = data.sca))
model.icc$`Sum Sq`[1] / sum(model.icc$`Sum Sq`)

# run full model
models = lmer(rating ~ instruction*`logistic classifier` + instruction*`regulate > rest` + instruction*`regulate > look` + (1 | subjectID), data = data.sca)

# run all possible nested models
models.sca = dredge(models, rank = "AIC", extra = "BIC") %>%
  select(AIC, delta, BIC, df, logLik, weight, `(Intercept)`, instruction, everything())

# set AIC for null model you want to compare model AIC values to
null = models.sca %>%
  arrange(df) %>%
  filter(instruction == "+" & df == 4)

# tidy for plotting
plot.data = models.sca %>%
  arrange(AIC) %>%
  mutate(specification = row_number(),
         better.fit = ifelse(AIC == null$AIC, "equal",
                      ifelse(AIC < null$AIC, "yes", "no")))

# order = plot.data %>%
#   arrange(AIC) %>%
#   mutate(better.fit.num = ifelse(better.fit == "yes", 1, 0)) %>%
#   gather(variable, value, -c(AIC, delta, BIC, df, logLik, weight, better.fit.num, specification, better.fit)) %>%
#   filter(!is.na(value)) %>%
#   group_by(variable) %>%
#   mutate(order = sum(better.fit.num)) %>%
#   select(variable, order) %>%
#   unique()

order = plot.data %>%
  gather(variable, value, -c(AIC, delta, BIC, df, logLik, weight, specification, better.fit)) %>%
  mutate(order = ifelse(grepl("^instruction", variable), 3,
                 ifelse(grepl(":instruction", variable), 1, 2))) %>%
  select(variable, order) %>%
  unique()

# variables included in model
variable.names = names(select(plot.data, -starts_with("better"), -specification, -AIC, -BIC, -df, -logLik, -delta, -weight, -`(Intercept)`))

# plot top panel
a = plot.data %>%
  ggplot(aes(specification, AIC, color = better.fit)) +
    geom_point(shape = "|", size = 4, alpha = .75) +
    geom_hline(yintercept = null$AIC, linetype = "dashed", color = "#5BBCD6") +
    scale_color_manual(values = c("#5BBCD6", "black", "#F43C13")) +
    labs(x = "", y = "AIC\n") +
    dc_bw +
    theme(legend.position = "none")
    # theme(#legend.title = element_text(size = 1),
    #       #legend.text = element_text(size = 9))

# set plotting order for variables based on number of times it's included in better fitting models
b = plot.data %>%
  gather(variable, value, eval(variable.names)) %>%
  left_join(., order, by = "variable") %>%
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = gsub("`regulate > look`", "regulate > look", variable),
         variable = gsub("`regulate > rest`", "regulate > rest", variable),
         variable = gsub("`logistic classifier`", "logistic classifier", variable),
         variable = gsub("regulate > look:instruction", "instruction:regulate > look", variable),
         variable = gsub("regulate > rest:instruction", "instruction:regulate > rest", variable),
         variable = gsub("logistic classifier:instruction", "instruction:logistic classifier", variable),
         variable = gsub("instruction:", "instruction  x  ", variable)) %>%
  ggplot(aes(specification, reorder(variable, order), color = better.fit)) +
    geom_text(aes(label = value), alpha = .75) +
    scale_color_manual(values = c("#5BBCD6", "black", "#F43C13")) +
    labs(x = "\nspecification number", y = "variables\n") +
    dc_bw +
    theme(legend.position = "none")
    # theme(#legend.title = element_text(size = 1),
    #       #legend.text = element_text(size = 9))

(plot.dev = plot_grid(a, b, ncol = 1, align = "v"))
```

## validation sample
```{r}
# set na.action for dredge
options(na.action = "na.fail")

# tidy data
data.sca = data %>%
  filter(sample == "far validation") %>%
  select(subjectID, trial, algorithm, dotSTD, rating, instruction) %>%
  spread(algorithm, dotSTD) %>%
  na.omit()

# ICC
model.icc = anova(lm(rating ~ subjectID, data = data.sca))
model.icc$`Sum Sq`[1] / sum(model.icc$`Sum Sq`)

# run full model
models = lmer(rating ~ instruction*`logistic classifier` + instruction*`regulate > rest` + instruction*`regulate > look` + (1 | subjectID), data = data.sca)

# run all possible nested models
models.sca = dredge(models, rank = "AIC", extra = "BIC") %>%
  select(AIC, delta, BIC, df, logLik, weight, `(Intercept)`, instruction, everything())

# set AIC for null model you want to compare model AIC values to
null = models.sca %>%
  arrange(df) %>%
  filter(instruction == "+" & df == 4)

# tidy for plotting
plot.data = models.sca %>%
  arrange(AIC) %>%
  mutate(specification = row_number(),
         better.fit = ifelse(AIC == null$AIC, "equal",
                      ifelse(AIC < null$AIC, "yes", "no")))

# order = plot.data %>%
#   arrange(AIC) %>%
#   mutate(better.fit.num = ifelse(better.fit == "yes", 1, 0)) %>%
#   gather(variable, value, -c(AIC, delta, BIC, df, logLik, weight, better.fit.num, specification, better.fit)) %>%
#   filter(!is.na(value)) %>%
#   group_by(variable) %>%
#   mutate(order = sum(better.fit.num)) %>%
#   select(variable, order) %>%
#   unique()

order = plot.data %>%
  gather(variable, value, -c(AIC, delta, BIC, df, logLik, weight, specification, better.fit)) %>%
  mutate(order = ifelse(grepl("^instruction", variable), 3,
                 ifelse(grepl(":instruction", variable), 1, 2))) %>%
  select(variable, order) %>%
  unique()

# variables included in model
variable.names = names(select(plot.data, -starts_with("better"), -specification, -AIC, -BIC, -df, -logLik, -delta, -weight, -`(Intercept)`))

# plot top panel
a = plot.data %>%
  ggplot(aes(specification, AIC, color = better.fit)) +
    geom_point(shape = "|", size = 4, alpha = .75) +
    geom_hline(yintercept = null$AIC, linetype = "dashed", color = "#5BBCD6") +
    scale_color_manual(values = c("#5BBCD6", "black", "#F43C13")) +
    labs(x = "", y = "AIC\n") +
    dc_bw +
    theme(legend.position = "none")
    # theme(#legend.title = element_text(size = 1),
    #       #legend.text = element_text(size = 9))

# set plotting order for variables based on number of times it's included in better fitting models
b = plot.data %>%
  gather(variable, value, eval(variable.names)) %>%
  left_join(., order, by = "variable") %>%
  mutate(value = ifelse(!is.na(value), "|", ""),
         variable = gsub("`regulate > look`", "regulate > look", variable),
         variable = gsub("`regulate > rest`", "regulate > rest", variable),
         variable = gsub("`logistic classifier`", "logistic classifier", variable),
         variable = gsub("regulate > look:instruction", "instruction:regulate > look", variable),
         variable = gsub("regulate > rest:instruction", "instruction:regulate > rest", variable),
         variable = gsub("logistic classifier:instruction", "instruction:logistic classifier", variable),
         variable = gsub("instruction:", "instruction  x  ", variable)) %>%
  ggplot(aes(specification, reorder(variable, order), color = better.fit)) +
    geom_text(aes(label = value), alpha = .75) +
    scale_color_manual(values = c("#5BBCD6", "black", "#F43C13")) +
    labs(x = "\nspecification number", y = "variables\n") +
    dc_bw +
    theme(legend.position = "none")
    # theme(#legend.title = element_text(size = 1),
    #       #legend.text = element_text(size = 9))

(plot.val = plot_grid(a, b, ncol = 1, align = "v"))
```

## combined
```{r, fig.width = 6, fig.height = 8}
plot_grid(plot.dev, plot.val, ncol = 1, align = "v", labels = c('A', 'B'))
```

